---
title: "Social Nets Data Prep"
date: "`r Sys.Date()`"
output: html_document
---

# Packages

```{r, warning=FALSE}
# required packages
library(tidyverse)
library(skimr)
library(purrr)
library(kableExtra)
library(knitr)
library(igraph)
library(corrr)
library(gridExtra)
library(lme4)
library(lmerTest)
```

# Analyses

## Load Data
```{r}
#Cleaned data file
main<-read_csv("FINAL.main.csv")

#Each row is a participant
subjects<-read_csv("FINAL.subjects.csv")

#Friendship Nomination Data
mainReg<-read_csv("FINAL.mainReg.csv")

#Avoidance Nomination Data
mainRegNeg<-read_csv("FINAL.mainRegNeg.csv")

# Raw Tie Data for Part 2
negMain <- read_csv('FINAL.enemiesLong.csv')

onlyMH<-subjects%>%
    filter(relig %in% c('Hindu','Muslim'))%>%
    droplevels()

```



## Grade Level Overviews

### Part 1: General Overview of Socio-Cognitive Survey Measures

#### Group Attitudes

```{r, warning=FALSE}

#Creates a long data frame of participant attitudes to various groups
#TargetF is the factorized version of the variable

attitudesLong <- subjects %>%
  select(Subject.ID,grade,Gender,relig,ageinyears,Attitudes_BadMarks:Attitudes_Rich) %>%
  gather(target,rating,Attitudes_BadMarks:Attitudes_Rich) %>%
  mutate(target = substr(target,11,20),
         targetF = factor(target,levels = c('Hindus','Muslims','Boys','Girls','GoodMarks','BadMarks','MyCaste','OtherCaste','MyLang','OtherLang','Rich','Poor')))

attitudesLong %>%
  group_by(targetF) %>%
  dplyr::summarise(avg=mean(rating,na.rm=T))

# Filter and split data
attLong_gender <- attitudesLong %>%
  filter(!is.na(Gender), !is.na(rating), targetF %in% c("Boys", "Girls"))
attLong_relig <- attitudesLong %>%
  filter(!is.na(relig), !is.na(rating), target %in% c("Hindus", "Muslims"))
```

```{r, warning=FALSE}
library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(grid)  # for unit()

# Define target categories of interest and ensure factor order
targets_of_interest <- c('GoodMarks', 'BadMarks', 'MyCaste', 'OtherCaste',
                         'MyLang', 'OtherLang', 'Poor', 'Rich')

attitudesLong <- attitudesLong %>%
  filter(target %in% targets_of_interest) %>%
  mutate(targetF = factor(target, levels = targets_of_interest))

# Define custom colors for jitter dots
# Define custom colors by thematic pairs
target_colors <- c(
  "GoodMarks"   = "steelblue1",  # light blue
  "BadMarks"  = "steelblue3",  # dark blue
  "MyCaste"    = "sienna1",  # light purple
  "OtherCaste" = "sienna3",  # dark purple
  "MyLang"     = "palegreen1",  # light brown
  "OtherLang"  = "palegreen3",  # dark brown
  "Poor"       = "pink1",  # light pink
  "Rich"       = "pink3"   # dark pink
)

# Compute means for labeling
mean_labels <- attitudesLong %>%
  group_by(targetF) %>%
  dplyr::summarise(mean_rating = mean(rating, na.rm = TRUE)) %>%
  mutate(label_y = mean_rating + 0.2)  # optional nudge upward

# Create the plot
combined_plot<-ggplot(attitudesLong, aes(x = targetF, y = rating, color = targetF)) +
  geom_jitter(width = 0.05, height = 0.15, size = 3, alpha = 0.6) +  # colored dots
  geom_violin(color = "black", fill = NA, linewidth = 0.5, width = 0.5) +  # transparent violin
  geom_boxplot(color = "black", fill = NA, width = 0.4, outlier.shape = NA) +  # boxplot
  stat_summary(fun = mean, geom = "point", shape = 18, size = 3, color = "darkred") +  # red mean point
  geom_label(
    data = mean_labels,
    aes(x = targetF, y = mean_rating, label = round(mean_rating, 2)),
    inherit.aes = FALSE,
    nudge_x = 0.25,
    size = 3,
    fill = "white",
    color = "black",
    label.size = 0.25,
    label.r = unit(0.15, "lines")
  ) +
  scale_color_manual(values = target_colors) +
  scale_y_continuous(breaks = seq(1, 7, 1), limits = c(1, 7.5)) +
  theme_bw() +
  xlab("Attitude Target") +
  ylab("Liking \n (1=Dislike Very Much; 7 = Like Very Much)") +
  ggtitle("Ratings of Ingroup and Outgroup \n Caste and Language Targets and other Social Categories") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
  )

# Show
print(combined_plot)

ggsave("combined_plot_ingroupoutgroupother.png",combined_plot,width=5.5,height=6,dpi=300)



```
##### Reported Linear Regressions

```{r}

summary(lm(Attitudes_Boys~grade*Gender*relig,data=onlyMH))

summary(lm(Attitudes_Girls~grade*Gender*relig,data=onlyMH))

summary(lm(Attitudes_Hindus~grade*Gender*relig,data=onlyMH))

summary(lm(Attitudes_Muslims~grade*Gender*relig,data=onlyMH))

```

```{r}
onlyMH$own_gender_pref <- ifelse(
    onlyMH$Gender == "M",
    onlyMH$Attitudes_Boys - onlyMH$Attitudes_Girls,
    onlyMH$Attitudes_Girls - onlyMH$Attitudes_Boys)
t.test(own_gender_pref ~ Gender, data = onlyMH)

onlyMH$own_religion_pref <- ifelse(
     onlyMH$relig == "Muslim",
     onlyMH$Attitudes_Muslims - onlyMH$Attitudes_Hindus,
     onlyMH$Attitudes_Hindus - onlyMH$Attitudes_Muslims
 )
t.test(own_religion_pref ~ relig, data = onlyMH)

t.test(own_gender_pref~relig,data=onlyMH)
t.test(own_religion_pref~Gender,data=onlyMH)
```


##### Age differences{.tabset}

###### Gender{.tabset}

```{r, warning=FALSE}
## Girls
cor.test(subjects$Attitudes_Girls,subjects$ageinyears)
# 0.14, p<0.001
## Boys
cor.test(subjects$Attitudes_Boys,subjects$ageinyears)
# 0.11, p<0.001

```

######  Religion {.tabset}

```{r, warning=FALSE}
#Muslims
cor.test(subjects$Attitudes_Muslims,subjects$ageinyears)
#0.31, p<0.001
#Hindus
cor.test(subjects$Attitudes_Hindus,subjects$ageinyears)
#0.19, p<0.001
```

###### Marks {.tabset}

```{r, warning=FALSE}
#Bad Marks
cor.test(subjects$Attitudes_BadMarks,subjects$ageinyears)
#0.28, p<0.01

#Good Marks
cor.test(subjects$Attitudes_GoodMarks,subjects$ageinyears)
#-0.16,p<0.01

```

###### Caste {.tabset}

```{r, warning=FALSE}
## My Caste
cor.test(subjects$Attitudes_MyCaste,subjects$ageinyears)
# 0.11, p<0.001

## Other Caste
cor.test(subjects$Attitudes_OtherCaste,subjects$ageinyears)
# 0.34, p<0.001
```

###### Language {.tabset}

```{r, warning=FALSE}
# My Language
cor.test(subjects$Attitudes_MyLang,subjects$ageinyears)
#-0.04, p=0.14

# Other Language
cor.test(subjects$Attitudes_OtherLang,subjects$ageinyears)
#0.29, p<0.001
```

###### Money{.tabset}

```{r, warning=FALSE}
#Poor
cor.test(subjects$Attitudes_Poor,subjects$ageinyears)
# 0.12, p<0.01
#Rich
cor.test(subjects$Attitudes_Rich,subjects$ageinyears)
#0.04, p=0.16
```

##### Gender differences {.tabset}

###### Do they Exist? {.tabset}

```{r, warning=FALSE}
#ANOVAs to test: Marks, Caste, Lang, Money

# nest by targets (which will be the outcomes of subsequent analyses)
nested <- attitudesLong %>% 
  filter(!is.na(Gender)) %>%
  group_by(target) %>%
  nest()

# run the anova on each data frame (the data in the 3rd column)
# map takes the data column, runs the analysis on the right, and saves results in the
# new column created by mutate
nested <- nested %>%
  mutate(model = map(data, ~aov(rating ~ Gender, data = .)))

# this creates a new column which is a dataframe of all the anova output
# nicely tidied up so you get the test statistics for each term
nested <- nested %>%
  mutate(tidy = map(model, broom::tidy))

#Here are the results
nested %>%
  unnest(tidy)

##ANOVA about Gender 
nested2<-attLong_gender%>%
  filter(!is.na(Gender))%>%
  group_by(target)%>%
  nest()

nested2<-nested2%>%
  mutate(model=map(data,~aov(rating~Gender,data=.)))

nested2<-nested2%>%
  mutate(tidy=map(model,broom::tidy))

nested2%>%
  unnest(tidy,.drop=T)

##ANOVA about Religion 
nested3<-attLong_relig%>%
  filter(!is.na(Gender))%>%
  group_by(target)%>%
  nest()

nested3<-nested3%>%
  mutate(model=map(data,~aov(rating~Gender,data=.)))

nested3<-nested3%>%
  mutate(tidy=map(model,broom::tidy))

nested3%>%
  unnest(tidy,.drop=T)
library(dplyr)
library(tidyr)
library(purrr)
library(broom)

# Define a function to process each nested ANOVA result
process_nested <- function(nested_df, label) {
  nested_df %>%
    # Unnest the 'tidy' column, which contains the ANOVA results in a tidy dataframe format
    unnest(tidy, .drop = TRUE) %>%
    
    # Filter out the 'Residuals' row because we're interested only in the model terms
    filter(term != "Residuals") %>%
    
    # Select relevant columns: the grouping variable 'target', the term tested (e.g., Gender), 
    # the test statistic (F value), and the p-value
    select(target, term, statistic, p.value) %>%
    
    # Rename the 'statistic' column to 'F' for clarity (since it's the F-test statistic)
    dplyr::rename(F = statistic) %>%
    
    # Convert the 'F' and 'p.value' columns into a long format, creating two rows per target-term pair
    gather(key = tmp, value = value, F, p.value) %>%
    
    # Unite the 'term' and 'tmp' columns into a single column (e.g., "Gender_F" or "Gender_p.value")
    unite(tmp, term, tmp, sep = ".") %>%
    
    # Spread the data back into wide format so that F and p.value are columns named by term
    spread(key = tmp, value = value) %>%
    
    # Add a new column 'source' to indicate which nested dataset this summary came from
    mutate(source = label)
}

# Apply the processing function to each nested ANOVA dataset,
# labeling them for identification
tab1 <- process_nested(nested, "nested1")
tab2 <- process_nested(nested2, "nested2")
tab3 <- process_nested(nested3, "nested3")

# Combine all the processed tables into one by stacking rows together
combined_tab <- bind_rows(tab1, tab2, tab3)

# Print the combined results table to view all ANOVA summaries from the three nested datasets
print(combined_tab)

library(dplyr)
library(gt)

combined_tab_color<-combined_tab %>%
  mutate(
    Gender.p.value = signif(Gender.p.value, 2)
  ) %>%
  gt() %>%
  fmt_number(
    columns = c("Gender.F", "Gender.p.value"),
    decimals = 2
  ) %>%
  data_color(
    columns = "Gender.p.value",
    colors = scales::col_bin(
      bins = c(-Inf, 0.05, Inf),
      palette = c("red", "black")
    )
  ) %>%
  cols_label(
    target = "Target",
    Gender.F = "F Statistic",
    Gender.p.value = "p-value"
  ) %>%
  tab_options(
    table.font.size=px(10)
  )

print(combined_tab_color)



```

###### Direction? {.tabset}

####### Good Marks {.tabset}

```{r, warning=FALSE}
t.test(subjects$Attitudes_GoodMarks~subjects$Gender) # F > M, p=0.004
effsize::cohen.d(subjects$Attitudes_GoodMarks~subjects$Gender) #d=0.19
```

###### My Caste {.tabset}

```{r, warning=FALSE}
t.test(subjects$Attitudes_MyCaste~subjects$Gender) # F > M, p=0.0175
effsize::cohen.d(subjects$Attitudes_MyCaste~subjects$Gender) #d=0.135
```
###### My Lang {.tabset}

```{r, warning=FALSE}
t.test(subjects$Attitudes_MyLang~subjects$Gender) # F > M, p=0.003
effsize::cohen.d(subjects$Attitudes_MyLang~subjects$Gender) #d=0.168
```
###### Boys {.tabset}

```{r, warning=FALSE}
t.test(subjects$Attitudes_Boys~subjects$Gender) # F << M, p<0.00001
effsize::cohen.d(subjects$Attitudes_Boys~subjects$Gender) #d=-1.69
```
###### Girls {.tabset}

```{r, warning=FALSE}
t.test(subjects$Attitudes_Girls~subjects$Gender) # F >> M, p<0.001
effsize::cohen.d(subjects$Attitudes_Girls~subjects$Gender) #d=1.37
```
##### Religious differences{.tabset}

###### Do they Exist? {.tabset}

```{r, warning=FALSE}
# nest by targets (which will be the outcomes of subsequent analyses)
nested <- attitudesLong %>% 
  filter(relig %in% c('Hindu','Muslim')) %>%
  group_by(target) %>%
  nest()

# run the anova on each data frame (the data in the 3rd column)
# map takes the data column, runs the analysis on the right, and saves results in the
# new column created by mutate
nested <- nested %>%
  mutate(model = map(data, ~aov(rating ~ relig, data = .)))

# this creates a new column which is a dataframe of all the anova output
# nicely tidied up so you get the test statistics for each term
nested <- nested %>%
  mutate(tidy = map(model, broom::tidy))

#Here are the results
nested %>%
  unnest(tidy)

##ANOVA about Gender 
nested2<-attLong_gender%>%
  filter(relig %in% c('Hindu','Muslim')) %>%
  group_by(target)%>%
  nest()

nested2<-nested2%>%
  mutate(model=map(data,~aov(rating~relig,data=.)))

nested2<-nested2%>%
  mutate(tidy=map(model,broom::tidy))

nested2%>%
  unnest(tidy,.drop=T)

##ANOVA about Religion 
nested3<-attLong_relig%>%
  filter(relig %in% c('Hindu','Muslim')) %>%
  group_by(target)%>%
  nest()

nested3<-nested3%>%
  mutate(model=map(data,~aov(rating~relig,data=.)))

nested3<-nested3%>%
  mutate(tidy=map(model,broom::tidy))

nested3%>%
  unnest(tidy,.drop=T)

# Apply the processing function to each nested ANOVA dataset,
# labeling them for identification
tab1 <- process_nested(nested, "nested1")
tab2 <- process_nested(nested2, "nested2")
tab3 <- process_nested(nested3, "nested3")

# Combine all the processed tables into one by stacking rows together
combined_tab <- bind_rows(tab1, tab2, tab3)

# Print the combined results table to view all ANOVA summaries from the three nested datasets
print(combined_tab)

library(dplyr)
library(gt)

combined_tab_color<-combined_tab %>%
  mutate(
    relig.p.value = signif(relig.p.value, 2)
  ) %>%
  gt() %>%
  fmt_number(
    columns = c("relig.F", "relig.p.value"),
    decimals = 2
  ) %>%
  data_color(
    columns = "relig.p.value",
    colors = scales::col_bin(
      bins = c(-Inf, 0.05, Inf),
      palette = c("red", "black")
    )
  ) %>%
  cols_label(
    target = "Target",
    relig.F = "F Statistic",
    relig.p.value = "p-value"
  ) %>%
  tab_options(
    table.font.size=px(10)
  )

print(combined_tab_color)



```


###### Direction? {.tabset}

####### Good Marks {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$Attitudes_GoodMarks~onlyMH$relig) # H > M, p=0.002
effsize::cohen.d(onlyMH$Attitudes_GoodMarks~onlyMH$relig) #d=0.214
```
####### MyLang {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$Attitudes_MyLang~onlyMH$relig) # H > M, p<0.001
effsize::cohen.d(onlyMH$Attitudes_MyLang~onlyMH$relig) #d=0.235
```
####### OtherLang {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$Attitudes_OtherLang~onlyMH$relig) # H > M, p=0.028
effsize::cohen.d(onlyMH$Attitudes_OtherLang~onlyMH$relig) #d=0.13
```
####### Rich {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$Attitudes_Rich~onlyMH$relig) # H > M, p=0.005
effsize::cohen.d(onlyMH$Attitudes_Rich~onlyMH$relig) #d=0.2054
```
####### Hindus {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$Attitudes_Hindus~onlyMH$relig) # H >> M, p<0.001
effsize::cohen.d(onlyMH$Attitudes_Hindus~onlyMH$relig) #d=1.80
```
####### Muslims {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$Attitudes_Muslims~onlyMH$relig) # H << M, p<0.001
effsize::cohen.d(onlyMH$Attitudes_Muslims~onlyMH$relig) #d=-1.378
```

#### Social Identity Importance
```{r, warning=FALSE}
# convert to long
identLong <- subjects %>%
  select(Subject.ID,grade,Gender,relig,ageinyears,Identification_Caste:Identification_School) %>%
  gather(target,rating,Identification_Caste:Identification_School) %>%
  mutate(target = substr(target,16,25),
         ident = 6-rating)
```

```{r, warning=FALSE}
library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(grid)  # for unit()

# Define target categories of interest and ensure factor order
targets_of_interest <- c('Caste', 'Gender', 'Language', 'Marks',
                         'Religion', 'School')
target_colors <- brewer.pal(n = length(targets_of_interest), name = "Set2")
names(target_colors) <- targets_of_interest  # name them so it's clear

identLong <- identLong %>%
  filter(target %in% targets_of_interest) %>%
  mutate(targetF = factor(target, levels = targets_of_interest))

# Compute means for labeling
mean_labels <- identLong %>%
  group_by(targetF) %>%
  dplyr::summarise(mean_ident = mean(ident, na.rm = TRUE)) %>%
  mutate(label_y = mean_ident + 0.2)  # optional nudge upward

# Create the plot
combined_plot<-ggplot(identLong, aes(x = targetF, y = ident, color = targetF)) +
  geom_jitter(width = 0.05, height = 0.15, size = 3, alpha = 0.6) +  # colored dots
  geom_violin(color = "black", fill = NA, linewidth = 0.5, width = 0.5) +  # transparent violin
  geom_boxplot(color = "black", fill = NA, width = 0.4, outlier.shape = NA) +  # boxplot
  stat_summary(fun = mean, geom = "point", shape = 18, size = 3, color = "darkred") +  # red mean point
  geom_label(
    data = mean_labels,
    aes(x = targetF, y = mean_ident, label = round(mean_ident, 2)),
    inherit.aes = FALSE,
    nudge_x = 0.25,
    size = 3,
    fill = "white",
    color = "black",
    label.size = 0.25,
    label.r = unit(0.15, "lines")
  ) +
  scale_color_manual(values = target_colors) +
  scale_y_continuous(breaks = seq(1, 5, 1), limits = c(1, 5.5)) +
  theme_bw() +
  xlab("Identification Category") +
  ylab("Identification \n (1=Not at all important; 5 = Very important)") +
  ggtitle("Identification with Various Social Categories") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
  )

# Show
print(combined_plot)

ggsave("combined_plot_identity.png",combined_plot,width=5.5,height=6,dpi=300)

```

##### Reported Linear Regressions

```{r}
summary(lm(Identification_Gender~grade*Gender*relig,data=onlyMH))

summary(lm(Identification_Religion~grade*Gender*relig,data=onlyMH))

```

##### Age differences{.tabset}

###### Caste {.tabset}

```{r, warning=FALSE}
cor.test(subjects$Identification_Caste,subjects$ageinyears)
# 0.12, p=0.687
```

###### Gender {.tabset}

```{r, warning=FALSE}
cor.test(subjects$Identification_Gender,subjects$ageinyears)
# -0.135, p<0.001
#Hence as kids get older, more identification (remember all this is reverse coded)
```

###### Language {.tabset}

```{r, warning=FALSE}
cor.test(subjects$Identification_Language,subjects$ageinyears)
# 0.175, p<0.001
# Less identification with language over age
```

###### Marks {.tabset}

```{r, warning=FALSE}
cor.test(subjects$Identification_Marks,subjects$ageinyears)
# 0.12, p<0.001
#Older, less identification with marks
```

###### Religion {.tabset}

```{r, warning=FALSE}
cor.test(subjects$Identification_Religion,subjects$ageinyears)
# -0.067, p=0.02
# more identification with age
```

###### School{.tabset}

```{r, warning=FALSE}
cor.test(subjects$Identification_School,subjects$ageinyears)
# 0.14, p<0.001
# Older, less identification with school
```
##### Gender differences {.tabset}

```{r, warning=FALSE}
# by gender - not too much going on
identPlotGender <- ggplot(filter(identLong,!is.na(Gender)),aes(x=target,y=ident,group=Gender,fill=Gender))
identPlotGender + stat_summary(fun.y=mean, geom="bar", size=2,position = position_dodge()) +
  stat_summary(fun.data="mean_cl_boot", geom="linerange",position = position_dodge(.9)) +
  scale_y_continuous(breaks=seq(1,5,1)) +  coord_cartesian(ylim=c(1,5)) +
  theme_bw() + xlab("Identification Target") + ylab("Degree of identification")

```
###### Do they Exist? {.tabset}

```{r, warning=FALSE}
#ANOVAs to test: 

# nest by targets (which will be the outcomes of subsequent analyses)
nested <- identLong %>% 
  filter(!is.na(Gender)) %>%
  group_by(target) %>%
  nest()

# run the anova on each data frame (the data in the 3rd column)
# map takes the data column, runs the analysis on the right, and saves results in the
# new column created by mutate
nested <- nested %>%
  mutate(model = map(data, ~aov(ident ~ Gender, data = .)))

# this creates a new column which is a dataframe of all the anova output
# nicely tidied up so you get the test statistics for each term
nested <- nested %>%
  mutate(tidy = map(model, broom::tidy))

#Here are the results
nested %>%
  unnest(tidy)

library(dplyr)
library(tidyr)
library(purrr)
library(broom)

# Define a function to process each nested ANOVA result
process_nested <- function(nested_df, label) {
  nested_df %>%
    # Unnest the 'tidy' column, which contains the ANOVA results in a tidy dataframe format
    unnest(tidy) %>%
    
    # Filter out the 'Residuals' row because we're interested only in the model terms
    filter(term != "Residuals") %>%
    
    # Select relevant columns: the grouping variable 'target', the term tested (e.g., Gender), 
    # the test statistic (F value), and the p-value
    select(target, term, statistic, p.value) %>%
    
    # Rename the 'statistic' column to 'F' for clarity (since it's the F-test statistic)
    dplyr::rename(F = statistic) %>%
    
    # Convert the 'F' and 'p.value' columns into a long format, creating two rows per target-term pair
    gather(key = tmp, value = value, F, p.value) %>%
    
    # Unite the 'term' and 'tmp' columns into a single column (e.g., "Gender_F" or "Gender_p.value")
    unite(tmp, term, tmp, sep = ".") %>%
    
    # Spread the data back into wide format so that F and p.value are columns named by term
    spread(key = tmp, value = value) %>%
    
    # Add a new column 'source' to indicate which nested dataset this summary came from
    mutate(source = label)
}


tab1 <- process_nested(nested,"nested1")

# Print the combined results table to view all ANOVA summaries 
print(tab1)

library(dplyr)
library(gt)

tab1_color<-tab1 %>%
  mutate(
    Gender.p.value = signif(Gender.p.value, 2)
  ) %>%
  gt() %>%
  fmt_number(
    columns = c("Gender.F", "Gender.p.value"),
    decimals = 2
  ) %>%
  data_color(
    columns = "Gender.p.value",
    colors = scales::col_bin(
      bins = c(-Inf, 0.05, Inf),
      palette = c("red", "black")
    )
  ) %>%
  cols_label(
    target = "Target",
    Gender.F = "F Statistic",
    Gender.p.value = "p-value"
  ) %>%
  tab_options(
    table.font.size=px(10)
  )

print(tab1_color)

```
###### Direction? {.tabset}

####### Caste {.tabset}

```{r, warning=FALSE}
t.test(subjects$Identification_Caste~subjects$Gender) # F < M, p=0.03
effsize::cohen.d(subjects$Identification_Caste~subjects$Gender) #d=-0.12
```
####### Marks {.tabset}

```{r, warning=FALSE}
t.test(subjects$Identification_Marks~subjects$Gender) # F < M, p=0.009
effsize::cohen.d(subjects$Identification_Marks~subjects$Gender) #d=-0.14
```
####### Religion {.tabset}

```{r, warning=FALSE}
t.test(subjects$Identification_Religion~subjects$Gender) # F < M, p=0.02
effsize::cohen.d(subjects$Identification_Religion~subjects$Gender) #d=-0.13
```

##### Religious differences {.tabset}

```{r, warning=FALSE}
# by religion - suggests bigger diffs here!
identPlotRelig <- ggplot(filter(identLong,relig %in% c('Hindu','Muslim')),aes(x=target,y=ident,group=relig,fill=relig))
identPlotRelig + stat_summary(fun.y=mean, geom="bar", size=2,position = position_dodge()) +
  stat_summary(fun.data="mean_cl_boot", geom="linerange",position = position_dodge(.9)) +
  scale_y_continuous(breaks=seq(1,5,1)) +  coord_cartesian(ylim=c(1,5)) +
  theme_bw() + xlab("Identification Target") + ylab("Degree of identification")
```

###### Do they Exist? {.tabset}

```{r, warning=FALSE}
#ANOVAs to test: 

# nest by targets (which will be the outcomes of subsequent analyses)
nested <- identLong %>% 
  filter(relig %in% c('Hindu','Muslim')) %>%
  group_by(target) %>%
  nest()

# run the anova on each data frame (the data in the 3rd column)
# map takes the data column, runs the analysis on the right, and saves results in the
# new column created by mutate
nested <- nested %>%
  mutate(model = map(data, ~aov(ident ~ relig, data = .)))

# this creates a new column which is a dataframe of all the anova output
# nicely tidied up so you get the test statistics for each term
nested <- nested %>%
  mutate(tidy = map(model, broom::tidy))

#Here are the results
nested %>%
  unnest(tidy)

tab1 <- process_nested(nested,"nested1")

# Print the combined results table to view all ANOVA summaries 
print(tab1)

library(dplyr)
library(gt)

tab1_color<-tab1 %>%
  mutate(
    relig.p.value = signif(relig.p.value, 2)
  ) %>%
  gt() %>%
  fmt_number(
    columns = c("relig.F", "relig.p.value"),
    decimals = 2
  ) %>%
  data_color(
    columns = "relig.p.value",
    colors = scales::col_bin(
      bins = c(-Inf, 0.05, Inf),
      palette = c("red", "black")
    )
  ) %>%
  cols_label(
    target = "Target",
    relig.F = "F Statistic",
    relig.p.value = "p-value"
  ) %>%
  tab_options(
    table.font.size=px(10)
  )

print(tab1_color)

```
###### Direction? {.tabset}

```{r, warning=FALSE}
#Remember onlyMH is only Muslim and Hindu participants
```

####### Caste {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$Identification_Caste~onlyMH$relig) # H > M, p<0.001
effsize::cohen.d(onlyMH$Identification_Caste~onlyMH$relig) #d=0.32
#Caste mattered more for Muslims
```

####### Gender {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$Identification_Gender~onlyMH$relig) # H > M, p=0.0005
effsize::cohen.d(onlyMH$Identification_Gender~onlyMH$relig) #d=0.198
# Muslims identified more with gender
```

####### Marks {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$Identification_Marks~onlyMH$relig) # H < M, p=0.045
effsize::cohen.d(onlyMH$Identification_Marks~onlyMH$relig) #d=-0.118
#Hindus identified more with marks
```

####### Religion {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$Identification_Religion~onlyMH$relig) # H > M, p<0.001
effsize::cohen.d(onlyMH$Identification_Religion~onlyMH$relig) #d=0.407
#Muslims more religion
```

####### School {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$Identification_School~onlyMH$relig) # H < M, p<0.0201
effsize::cohen.d(onlyMH$Identification_School~onlyMH$relig) #d=-0.27
#Hindus identify more with school
```


#### Perception of School Norms
```{r, warning=FALSE}
# convert to long
normsLong <- subjects %>%
  dplyr::select(Subject.ID,grade,Gender,relig,ageinyears,SchoolHarmony_BoyGirl:SchoolHarmony_RichPoor) %>%
  gather(target,rating,SchoolHarmony_BoyGirl:SchoolHarmony_RichPoor) %>%
  mutate(target = substr(target,15,25),
         norm = 6-rating) #Note we're reverse coded again
```

```{r, warning=FALSE}
library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(grid)  # for unit()

# Define target categories of interest and ensure factor order
targets_of_interest <- c('BoyGirl', 'HinduMuslim', 'InterCaste', 'People',
                         'RichPoor')
target_colors <- brewer.pal(n = length(targets_of_interest), name = "Set2")
names(target_colors) <- targets_of_interest  # name them so it's clear

normsLong <- normsLong %>%
  filter(target %in% targets_of_interest) %>%
  mutate(targetF = factor(target, levels = targets_of_interest))

# Compute means for labeling
mean_labels <- normsLong %>%
  group_by(target) %>%
  dplyr::summarise(mean_norm = mean(norm, na.rm = TRUE)) %>%
  mutate(label_y = mean_norm + 0.2)  # optional nudge upward

# Create the plot
combined_plot<-ggplot(normsLong, aes(x = target, y = norm, color = target)) +
  geom_jitter(width = 0.05, height = 0.15, size = 3, alpha = 0.6) +  # colored dots
  geom_violin(color = "black", fill = NA, linewidth = 0.5, width = 0.5) +  # transparent violin
  geom_boxplot(color = "black", fill = NA, width = 0.4, outlier.shape = NA) +  # boxplot
  stat_summary(fun = mean, geom = "point", shape = 18, size = 3, color = "darkred") +  # red mean point
  geom_label(
    data = mean_labels,
    aes(x = target, y = mean_norm, label = round(mean_norm, 2)),
    inherit.aes = FALSE,
    nudge_x = 0.25,
    size = 3,
    fill = "white",
    color = "black",
    label.size = 0.25,
    label.r = unit(0.15, "lines")
  ) +
  scale_color_manual(values = target_colors) +
  scale_y_continuous(breaks = seq(1, 5, 1), limits = c(1, 5.5)) +
  theme_bw() +
  xlab("Groups of People") +
  ylab(" 'In my school, _____ get along well' \n (1=Definitely disagree; 5 = Definitely agree)") +
  ggtitle("School Norms of Groups Getting Along") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
  )

# Show
print(combined_plot)

ggsave("combined_plot_schoolnorms.png",combined_plot,width=5.5,height=6,dpi=300)

```

##### Reported Linear Regressions
```{r}
summary(lm(SchoolHarmony_BoyGirl~grade*Gender*relig,data=onlyMH))

summary(lm(SchoolHarmony_HinduMuslim~grade*Gender*relig,data=onlyMH))

summary(lm(SchoolHarmony_People~grade*Gender*relig,data=onlyMH))

```

##### Age differences {.tabset}

###### BoyGirl {.tabset}

```{r, warning=FALSE}
cor.test(subjects$SchoolHarmony_BoyGirl,subjects$ageinyears)
# -0.196, p<0.001
#older, more endorsement
```

###### HinduMuslim {.tabset}

```{r, warning=FALSE}
cor.test(subjects$SchoolHarmony_HinduMuslim,subjects$ageinyears)
#-0.256, p<0.001
#older, more endorsement
```

###### InterCaste {.tabset}

```{r, warning=FALSE}
cor.test(subjects$SchoolHarmony_InterCaste,subjects$ageinyears)
# -0.24, p<0.001
#older, more endorsement
```

###### People {.tabset}

```{r, warning=FALSE}
cor.test(subjects$SchoolHarmony_People,subjects$ageinyears)
#0.118, p<0.001
#older, less endorsement
```

###### RichPoor {.tabset}

```{r, warning=FALSE}
cor.test(subjects$SchoolHarmony_RichPoor,subjects$ageinyears)
#-0.155, p<0.001
# older, more endorsement

```
##### Gender differences {.tabset}

```{r, warning=FALSE}
# by gender - not too much going on
normsPlotGender <- ggplot(filter(normsLong,!is.na(Gender)),aes(x=target,y=norm,group=Gender,fill=Gender))
normsPlotGender + stat_summary(fun.y=mean, geom="bar", size=2,position = position_dodge()) +
  stat_summary(fun.data="mean_cl_boot", geom="linerange",position = position_dodge(.9)) +
  scale_y_continuous(breaks=seq(1,5,1)) +  coord_cartesian(ylim=c(1,5)) +
  theme_bw() + xlab("Norm Type") + ylab("Endorsement of Positive Norm")
```

###### Do they Exist? (No) {.tabset} 

```{r, warning=FALSE}
#ANOVAs to test: 

# nest by targets (which will be the outcomes of subsequent analyses)
nested <- normsLong %>% 
  filter(!is.na(Gender)) %>%
  group_by(target) %>%
  nest()

# run the anova on each data frame (the data in the 3rd column)
# map takes the data column, runs the analysis on the right, and saves results in the
# new column created by mutate
nested <- nested %>%
  mutate(model = map(data, ~aov(norm ~ Gender, data = .)))

# this creates a new column which is a dataframe of all the anova output
# nicely tidied up so you get the test statistics for each term
nested <- nested %>%
  mutate(tidy = map(model, broom::tidy))

#Here are the results
nested %>%
  unnest(tidy)

tab1 <- process_nested(nested,"nested1")

# Print the combined results table to view all ANOVA summaries 
print(tab1)

library(dplyr)
library(gt)

tab1_color<-tab1 %>%
  mutate(
    Gender.p.value = signif(Gender.p.value, 2)
  ) %>%
  gt() %>%
  fmt_number(
    columns = c("Gender.F", "Gender.p.value"),
    decimals = 2
  ) %>%
  data_color(
    columns = "Gender.p.value",
    colors = scales::col_bin(
      bins = c(-Inf, 0.05, Inf),
      palette = c("red", "black")
    )
  ) %>%
  cols_label(
    target = "Target",
    Gender.F = "F Statistic",
    Gender.p.value = "p-value"
  ) %>%
  tab_options(
    table.font.size=px(10)
  )

print(tab1_color)
```


##### Religious Differences {.tabset}

```{r, warning=FALSE}
# by religion - suggests bigger diffs here!
normsPlotRelig <- ggplot(filter(normsLong,relig %in% c('Hindu','Muslim')),aes(x=target,y=norm,group=relig,fill=relig))
normsPlotRelig + stat_summary(fun.y=mean, geom="bar", size=2,position = position_dodge()) +
  stat_summary(fun.data="mean_cl_boot", geom="linerange",position = position_dodge(.9)) +
  scale_y_continuous(breaks=seq(1,5,1)) +  coord_cartesian(ylim=c(1,5)) +
  theme_bw() + xlab("Norm Type") + ylab("Endorsement of Positive Norm")
```
###### Do they Exist? {.tabset}

```{r, warning=FALSE}
#ANOVAs to test: 

# nest by targets (which will be the outcomes of subsequent analyses)
nested <- normsLong %>% 
  filter(relig %in% c('Hindu','Muslim')) %>%
  group_by(target) %>%
  nest()

# run the anova on each data frame (the data in the 3rd column)
# map takes the data column, runs the analysis on the right, and saves results in the
# new column created by mutate
nested <- nested %>%
  mutate(model = map(data, ~aov(norm ~ relig, data = .)))

# this creates a new column which is a dataframe of all the anova output
# nicely tidied up so you get the test statistics for each term
nested <- nested %>%
  mutate(tidy = map(model, broom::tidy))

#Here are the results
nested %>%
  unnest(tidy)

tab1 <- process_nested(nested,"nested1")

# Print the combined results table to view all ANOVA summaries 
print(tab1)

library(dplyr)
library(gt)

tab1_color<-tab1 %>%
  mutate(
    relig.p.value = signif(relig.p.value, 2)
  ) %>%
  gt() %>%
  fmt_number(
    columns = c("relig.F", "relig.p.value"),
    decimals = 2
  ) %>%
  data_color(
    columns = "relig.p.value",
    colors = scales::col_bin(
      bins = c(-Inf, 0.05, Inf),
      palette = c("red", "black")
    )
  ) %>%
  cols_label(
    target = "Target",
    relig.F = "F Statistic",
    relig.p.value = "p-value"
  ) %>%
  tab_options(
    table.font.size=px(10)
  )
print(tab1_color)
```

###### Direction? {.tabset}

```{r, warning=FALSE}
#Remember onlyMH is only Muslim and Hindu participants
onlyMH<-subjects%>%
    filter(relig %in% c('Hindu','Muslim'))%>%
    droplevels()
```

####### BoyGirl {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$SchoolHarmony_BoyGirl~onlyMH$relig) # H < M, p=0.0038
effsize::cohen.d(onlyMH$SchoolHarmony_BoyGirl~onlyMH$relig) #d=-0.20
#Hindus perceived more BoyGirl harmony than Muslims
```

### Part 2: Social Network Overview

#### Summaries of number of ties {.tabset}

##### Positive Ties {.tabset}

```{r, warning=FALSE}
# positive ties
ties <- main %>%
  select(Subject.ID,grade,Gender,relig,Category,Response) %>%
  group_by(grade,Gender,relig,Subject.ID) %>%
  dplyr::summarise(numAlters = length(!is.na(Response)))

mean(ties$numAlters) # 6.27
sd(ties$numAlters) # 1.6
min(ties$numAlters)# 1 
max(ties$numAlters) # 23
table(ties$numAlters)

38+11+3+3+1+1  # number selecting more than 7 (57)

```

###### Differences by Age, Gender, Religion {.tabset}

####### Age {.tabset}

```{r, warning=FALSE}
cor.test(ties$grade,ties$numAlters)  # more ties with age (p<0.001)
```

####### Gender {.tabset}

```{r, warning=FALSE}
# gender or relig diffs?
t.test(ties$numAlters ~ ties$Gender) #(p=0.05) (F=6.17, M=6.34) 
effsize::cohen.d(ties$numAlters ~ ties$Gender) # d = -0.11 (negligible)
```
####### Religion {.tabset}

```{r, warning=FALSE}
t.test(numAlters ~ relig, data=filter(ties,relig %in% c('Hindu','Muslim'))) #(p=0.0477), H > M
  
effsize::cohen.d(numAlters ~ relig, data=droplevels(filter(ties,relig %in% c('Hindu','Muslim')))) # d = 0.11
```
##### Negative Ties {.tabset}

```{r, warning=FALSE}
negTies <- negMain %>%
  select(Subject.ID,grade,Gender,relig,Category,Response) %>%
  group_by(grade,Gender,relig,Subject.ID) %>%
  dplyr::summarise(numAlters = length(!is.na(Response)))


mean(negTies$numAlters) # 4.62
sd(negTies$numAlters) # 2.51
min(negTies$numAlters) # 1
max(negTies$numAlters) #15
table(negTies$numAlters)
10+3+3+1+2+1  # number selecting more than 7 (20)
```
######Differences by Age {.tabset}

#######Age (Grade) {.tabset}

```{r, warning=FALSE}
cor.test(negTies$grade,negTies$numAlters)  #p=0.77
```


#######Gender {.tabset}

```{r, warning=FALSE}
t.test(negTies$numAlters ~ negTies$Gender) # p=0.18

```

#######Religion {.tabset}

```{r, warning=FALSE}
t.test(numAlters ~ relig, data=filter(negTies,relig %in% c('Hindu','Muslim'))) #p=0.21
```
##### Positive & Negative Ties Correlated? {.tabset}

```{r, warning=FALSE}
# both ties
bothTies <- negTies %>% dplyr::rename(numNeg = numAlters) %>%
  left_join(ties)
```

```{r, warning=FALSE}
cor.test(bothTies$numAlters,bothTies$numNeg) # positive correlation
# p<0.001, r=0.21
```

#### (Own) Gender and Religion Composition {.tabset}

```{r, warning=FALSE}

propTies <- main %>%
  group_by(Gender,relig,grade,Subject.ID) %>%
  dplyr::summarise(numNom = length(Response),
            pctOG = mean(ownGender,na.rm=T),
            pctOR = mean(ownRelig,na.rm=T),
            allOG = ifelse(pctOG==1,1,0),
            allOR = ifelse(pctOR==1,1,0))
propTiesNeg <- negMain %>%
  group_by(Gender,relig,grade,Subject.ID) %>%
  dplyr::summarise(numNeg = length(Response),
            pctOGneg = mean(ownGender,na.rm=T),
            pctORneg = mean(ownRelig,na.rm=T),
            allOGneg = ifelse(pctOGneg==1,1,0),
            allORneg = ifelse(pctORneg==1,1,0))

propBoth <- propTies %>% 
  full_join(propTiesNeg) 
```

##### Summary Positive Ties {.tabset}

###### Own Gender {.tabset}

```{r, warning=FALSE}
mean(propBoth$pctOG,na.rm=T) # 0.95
sd(propBoth$pctOG,na.rm=T) # 0.13
mean(propBoth$allOG,na.rm=T) # 0.84
```
###### Own Religion {.tabset}

```{r, warning=FALSE}
mean(propBoth$pctOR,na.rm=T) #0.71
sd(propBoth$pctOR,na.rm=T) # 0.28
mean(propBoth$allOR,na.rm=T) # 0.29
```
##### Summary Negative Ties {.tabset}

###### Own Gender {.tabset}

```{r, warning=FALSE}
mean(propBoth$pctOGneg,na.rm=T) # 0.77
sd(propBoth$pctOGneg,na.rm=T) # 0.34
mean(propBoth$pctOGneg,na.rm=T) #0.77
```
###### Own Religion {.tabset}

```{r, warning=FALSE}
mean(propBoth$pctORneg,na.rm=T) #0.42
sd(propBoth$pctORneg,na.rm=T) #0.35
mean(propBoth$pctORneg,na.rm=T) #0.42
```
##### Differences {.tabset}

###### Age (Grade Differences) {.tabset}

```{r, warning=FALSE}
# grade comparisons
cor.test(propBoth$pctOG,propBoth$grade) #p<0.001
# more age, less own gender prop networks, r = -0.12

cor.test(propBoth$pctOGneg,propBoth$grade)  # p=0.39

cor.test(propBoth$pctOR,propBoth$grade) #p=0.002
# more age, less own religion prop networks, r = -0.08

cor.test(propBoth$pctORneg,propBoth$grade)  # p = 0.5
```

###### Gender Differences {.tabset}

```{r, warning=FALSE}
t.test(propBoth$pctOG ~ propBoth$Gender) #(p<0.001)
# More M than F positive OG
t.test(propBoth$pctOGneg ~ propBoth$Gender)#(p<0.001)
# More M than F negative OG
t.test(propBoth$pctOR ~ propBoth$Gender)#(p<0.001)
# More M than F positive OR
t.test(propBoth$pctORneg ~ propBoth$Gender)#(p=0.002)
# More F than M negative OR
```
###### Religion Differences {.tabset}

```{r, warning=FALSE}
# restrict to Hindu and Muslim for religion comparisons
propBothHR <- filter(propBoth,relig %in% c('Muslim','Hindu'))

t.test(propBothHR$pctOG ~ propBothHR$relig) # ns, p=0.14
t.test(propBothHR$pctOGneg ~ propBothHR$relig)  # ns, p = 0.05
#Hindus more than Muslims own gender (marginal)

t.test(propBothHR$pctOR ~ propBothHR$relig) # sig, p<0.001
# Hindus had more own religion friends than Muslims

t.test(propBothHR$pctORneg ~ propBothHR$relig)  # sig, p<0.001
#Hindus had more negative own religion than Muslims
```

#### Basic Visualizations {.tabset}

```{r, warning=FALSE}
#loading in graph objects and related setup (need to do one at a time)
load('allgraphsFinal.RData')
allgraphs<-lapply(allgraphs,igraph::upgrade_graph)
```

```{r, warning=FALSE}
#loading in graph objects and related setup (need to do one at a time)
load('allgraphsNegFinal.RData')
allgraphsNeg<-lapply(allgraphsNeg,igraph::upgrade_graph)
```
##### Positive Graphs {.tabset}

###### One Grade 3 Classroom {.tabset}

```{r, warning=FALSE}
library(dplyr)
library(igraph)
library(ggraph)
#Selects the classroom
graph1 <- allgraphs[[1]]


graph1 <- graph1 %>%
# adds or updates a vertex attribute called "Religion" based on "hindu" attribute
  ## For each vertex -- if Hindu is NA -- Other/Unknown, 1 -- Hindu, Otherwise -- Muslim
  igraph::set_vertex_attr(
    "Religion",
    index = V(graph1), # all vertices of graph1
    ifelse(
        is.na(vertex_attr(graph1)$hindu),'Other / Unknown',
        ifelse(vertex_attr(graph1)$hindu==1,'Hindu','Muslim')))

# Create a graph using the Kamada-Kawai (kk) layout
ggraph::ggraph(graph1, layout = 'kk') + 
  #Draw edges with arrows
  geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm'), colour='grey') + 
  geom_edge_loop(colour='grey') +
  #Color nodes is thegender (as based on male)
  #Shape made by religion
  geom_node_point(aes(color = as.factor(male),shape=Religion), size=6) +
  theme_graph(foreground = 'steelblue', fg_text_colour = 'white') +
  labs(title='A 3rd Grade Classroom') +
  scale_color_manual(
    values = c("0" = "goldenrod1", "1" = "mediumpurple1"), 
    breaks = c("0", "1"),
    labels = c("Female", "Male"),
    name = "Gender"
  )+
  #scale_color_discrete(breaks=c(0,1),labels=c("Female","Male"), name='Gender')+
  theme(text=element_text(family="Calibri"))

ggraph::ggraph(graph1, layout = 'kk') + 
  geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm'), colour = 'grey') + 
  geom_edge_loop(colour = 'grey') +
  geom_node_point(aes(color = Religion, shape = as.factor(male)), size = 6) +
  theme_graph(foreground = 'steelblue', fg_text_colour = 'white') +
  labs(title = 'A 3rd Grade Classroom') +
  scale_color_manual(
    values = c(
      "Hindu" = "tomato",
      "Muslim" = "deepskyblue",
      "Other / Unknown" = "gray70"
    ),
    name = "Religion"
  ) +
  scale_shape_manual(
    values = c("0" = 16, "1" = 17),
    labels = c("Female", "Male"),
    name = "Gender"
  ) +
  theme(text = element_text(family = "Calibri"))

#Reciprocity of the graph (proportion of mutual edges, I nominate you, you nominate me)
reciprocity(graph1) # 0.46
```


###### One Grade 6 Classroom {.tabset}

```{r, warning=FALSE}
library(dplyr)
library(igraph)
library(ggraph)
#Selects the classroom
graph2 <- allgraphs[[11]]


graph2 <- graph2 %>%
# adds or updates a vertex attribute called "Religion" based on "hindu" attribute
  ## For each vertex -- if Hindu is NA -- Other/Unknown, 1 -- Hindu, Otherwise -- Muslim
  igraph::set_vertex_attr(
    "Religion",
    index = V(graph2), # all vertices of graph2
    ifelse(
        is.na(vertex_attr(graph2)$hindu),'Other / Unknown',
        ifelse(vertex_attr(graph2)$hindu==1,'Hindu','Muslim')))

# Create a graph using the Kamada-Kawai (kk) layout
ggraph::ggraph(graph2, layout = 'kk') + 
  #Draw edges with arrows
  geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm'), colour='grey') + 
  geom_edge_loop(colour='grey') +
  #Color nodes is thegender (as based on male)
  #Shape made by religion
  geom_node_point(aes(color = as.factor(male),shape=Religion), size=6) +
  theme_graph(foreground = 'steelblue', fg_text_colour = 'white') +
  labs(title='A 6th Grade Classroom') +
  scale_color_manual(
    values = c("0" = "goldenrod1", "1" = "mediumpurple1"), 
    breaks = c("0", "1"),
    labels = c("Female", "Male"),
    name = "Gender"
  )+
  #scale_color_discrete(breaks=c(0,1),labels=c("Female","Male"), name='Gender')+
  theme(text=element_text(family="Calibri"))

ggraph::ggraph(graph2, layout = 'kk') + 
  geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm'), colour = 'grey') + 
  geom_edge_loop(colour = 'grey') +
  geom_node_point(aes(color = Religion, shape = as.factor(male)), size = 6) +
  theme_graph(foreground = 'steelblue', fg_text_colour = 'white') +
  labs(title = 'A 6th Grade Classroom') +
  scale_color_manual(
    values = c(
      "Hindu" = "tomato",
      "Muslim" = "deepskyblue",
      "Other / Unknown" = "gray70"
    ),
    name = "Religion"
  ) +
  scale_shape_manual(
    values = c("0" = 16, "1" = 17),
    labels = c("Female", "Male"),
    name = "Gender"
  ) +
  theme(text = element_text(family = "Calibri"))

#Reciprocity of the graph (proportion of mutual edges, I nominate you, you nominate me)
reciprocity(graph2) # 0.44
```


```{r}
ggraph::ggraph(graph2, layout = 'kk') + 
  # Draw edges
  geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm'), colour = 'grey') + 
  geom_edge_loop(colour = 'grey') +

  # Nodes: fill = gender, border color = religion
  geom_node_point(
    aes(
      fill = as.factor(male),   # Fill color by gender
      color = Religion          # Border color by religion
    ),
    shape = 21,                 # Circle with border and fill
    stroke = 2,               # Border thickness
    size = 3
  ) +

  theme_graph(foreground = 'black', fg_text_colour = 'white') +
  labs(title = 'A 6th Grade Classroom') +

  # Gender fill colors
  scale_fill_manual(
    values = c("0" = "lightcoral", "1" = "lightblue1"), 
    breaks = c("0", "1"),
    labels = c("Female", "Male"),
    name = "Gender"
  ) +

  # Religion border colors
  scale_color_manual(
    values = c(
      "Muslim" = "springgreen4",
      "Hindu" = "tan1",
      "Other / Unknown" = "gray70"
    ),
    name = "Religion"
  ) +

  theme(text = element_text(family = "Calibri"))


ggraph::ggraph(graph2, layout = 'kk') + 
  # Draw edges
  geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm'), colour = 'grey') + 
  geom_edge_loop(colour = 'grey') +

  # Nodes: fill = gender, shape = gender, border color = religion
  geom_node_point(
    aes(
      fill = as.factor(male),    # Fill color by gender
      shape = as.factor(male),   # Shape by gender
      color = Religion           # Border color by religion
    ),
    stroke = 2,               # Border thickness
    size = 4
  ) +

  theme_graph(foreground = 'black', fg_text_colour = 'white') +
  labs(title = 'A 6th Grade Classroom') +

  # Gender fill colors
  scale_fill_manual(
    values = c("0" = "lightcoral", "1" = "lightblue1"), 
    breaks = c("0", "1"),
    labels = c("Female", "Male"),
    name = "Gender"
  ) +

  # Gender shapes: Female = triangle (24), Male = square (22)
  scale_shape_manual(
    values = c("0" = 24, "1" = 22), 
    breaks = c("0", "1"),
    labels = c("Female", "Male"),
    name = "Gender"
  ) +

  # Religion border colors
  scale_color_manual(
    values = c(
      "Muslim" = "springgreen4",
      "Hindu" = "tan1",
      "Other / Unknown" = "gray70"
    ),
    name = "Religion"
  ) +

  theme(text = element_text(family = "Calibri"))


```


###### One Grade 9 Classroom {.tabset}

```{r, warning=FALSE}
library(dplyr)
library(igraph)
library(ggraph)
#Selects the classroom
graph3 <- allgraphs[[19]]


graph3 <- graph3 %>%
# adds or updates a vertex attribute called "Religion" based on "hindu" attribute
  ## For each vertex -- if Hindu is NA -- Other/Unknown, 1 -- Hindu, Otherwise -- Muslim
  igraph::set_vertex_attr(
    "Religion",
    index = V(graph3), # all vertices of graph3
    ifelse(
        is.na(vertex_attr(graph3)$hindu),'Other / Unknown',
        ifelse(vertex_attr(graph3)$hindu==1,'Hindu','Muslim')))

# Create a graph using the Kamada-Kawai (kk) layout
ggraph::ggraph(graph3, layout = 'kk') + 
  #Draw edges with arrows
  geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm'), colour='grey') + 
  geom_edge_loop(colour='grey') +
  #Color nodes is thegender (as based on male)
  #Shape made by religion
  geom_node_point(aes(color = as.factor(male),shape=Religion), size=6) +
  theme_graph(foreground = 'steelblue', fg_text_colour = 'white') +
  labs(title='A 9th Grade Classroom') +
  scale_color_manual(
    values = c("0" = "goldenrod1", "1" = "mediumpurple1"), 
    breaks = c("0", "1"),
    labels = c("Female", "Male"),
    name = "Gender"
  )+
  theme(text=element_text(family="Calibri"))

ggraph::ggraph(graph3, layout = 'kk') + 
  geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm'), colour = 'grey') + 
  geom_edge_loop(colour = 'grey') +
  geom_node_point(aes(color = Religion, shape = as.factor(male)), size = 6) +
  theme_graph(foreground = 'steelblue', fg_text_colour = 'white') +
  labs(title = 'A 9th Grade Classroom') +
  scale_color_manual(
    values = c(
      "Hindu" = "tomato",
      "Muslim" = "deepskyblue",
      "Other / Unknown" = "gray70"
    ),
    name = "Religion"
  ) +
  scale_shape_manual(
    values = c("0" = 16, "1" = 17),
    labels = c("Female", "Male"),
    name = "Gender"
  ) +
  theme(text = element_text(family = "Calibri"))

#Reciprocity of the graph (proportion of mutual edges, I nominate you, you nominate me)
reciprocity(graph3) # 0.46
```

##### Negative Graphs {.tabset}

###### One Grade 5 Classroom {.tabset}

```{r, warning=FALSE}
library(dplyr)
library(igraph)
library(ggraph)
#Selects the classroom
graph1neg <- allgraphsNeg[[1]]


graph1neg <- graph1neg %>%
# adds or updates a vertex attribute called "Religion" based on "hindu" attribute
  ## For each vertex -- if Hindu is NA -- Other/Unknown, 1 -- Hindu, Otherwise -- Muslim
  igraph::set_vertex_attr(
    "Religion",
    index = V(graph1neg), # all vertices of graph1neg
    ifelse(
        is.na(vertex_attr(graph1neg)$hindu),'Other / Unknown',
        ifelse(vertex_attr(graph1neg)$hindu==1,'Hindu','Muslim')))

# Create a graph using the Kamada-Kawai (kk) layout
ggraph::ggraph(graph1neg, layout = 'kk') + 
  #Draw edges with arrows
  geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm'), colour='grey') + 
  geom_edge_loop(colour='grey') +
  #Color nodes is thegender (as based on male)
  #Shape made by religion
  geom_node_point(aes(color = as.factor(male),shape=Religion), size=6) +
  theme_graph(foreground = 'steelblue', fg_text_colour = 'white') +
  labs(title='A 5th Grade Classroom: Negative Ties') +
  scale_color_manual(
    values = c("0" = "goldenrod1", "1" = "mediumpurple1"), 
    breaks = c("0", "1"),
    labels = c("Female", "Male"),
    name = "Gender"
  )+
  #scale_color_discrete(breaks=c(0,1),labels=c("Female","Male"), name='Gender')+
  theme(text=element_text(family="Calibri"))

ggraph::ggraph(graph1neg, layout = 'kk') + 
  geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm'), colour = 'grey') + 
  geom_edge_loop(colour = 'grey') +
  geom_node_point(aes(color = Religion, shape = as.factor(male)), size = 6) +
  theme_graph(foreground = 'steelblue', fg_text_colour = 'white') +
  labs(title = 'A 5th Grade Classroom: Negative Ties') +
  scale_color_manual(
    values = c(
      "Hindu" = "tomato",
      "Muslim" = "deepskyblue",
      "Other / Unknown" = "gray70"
    ),
    name = "Religion"
  ) +
  scale_shape_manual(
    values = c("0" = 16, "1" = 17),
    labels = c("Female", "Male"),
    name = "Gender"
  ) +
  theme(text = element_text(family = "Calibri"))

#Reciprocity of the graph (proportion of mutual edges, I nominate you, you nominate me)
reciprocity(graph1neg) # 0.1

```

```{r}

ggraph::ggraph(graph1neg, layout = 'kk') + 
  # Draw edges
  geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm'), colour = 'grey') + 
  geom_edge_loop(colour = 'grey') +

  # Nodes: fill = gender, shape = gender, border color = religion
  geom_node_point(
    aes(
      fill = as.factor(male),    # Fill color by gender
      shape = as.factor(male),   # Shape by gender
      color = Religion           # Border color by religion
    ),
    stroke = 2,               # Border thickness
    size = 4
  ) +

  theme_graph(foreground = 'black', fg_text_colour = 'white') +
  labs(title = 'A 7th Grade Classroom Negative Ties') +

  # Gender fill colors
  scale_fill_manual(
    values = c("0" = "lightcoral", "1" = "lightblue1"), 
    breaks = c("0", "1"),
    labels = c("Female", "Male"),
    name = "Gender"
  ) +

  # Gender shapes: Female = triangle (24), Male = square (22)
  scale_shape_manual(
    values = c("0" = 24, "1" = 22), 
    breaks = c("0", "1"),
    labels = c("Female", "Male"),
    name = "Gender"
  ) +

  # Religion border colors
  scale_color_manual(
    values = c(
      "Muslim" = "springgreen4",
      "Hindu" = "tan1",
      "Other / Unknown" = "gray70"
    ),
    name = "Religion"
  ) +

  theme(text = element_text(family = "Calibri"))

```


###### One Grade 7 Classroom {.tabset}

```{r, warning=FALSE}
library(dplyr)
library(igraph)
library(ggraph)
#Selects the classroom
graph2neg <- allgraphsNeg[[7]]


graph2neg <- graph2neg %>%
# adds or updates a vertex attribute called "Religion" based on "hindu" attribute
  ## For each vertex -- if Hindu is NA -- Other/Unknown, 1 -- Hindu, Otherwise -- Muslim
  igraph::set_vertex_attr(
    "Religion",
    index = V(graph2neg), # all vertices of graph2neg
    ifelse(
        is.na(vertex_attr(graph2neg)$hindu),'Other / Unknown',
        ifelse(vertex_attr(graph2neg)$hindu==1,'Hindu','Muslim')))

# Create a graph using the Kamada-Kawai (kk) layout
ggraph::ggraph(graph2neg, layout = 'kk') + 
  #Draw edges with arrows
  geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm'), colour='grey') + 
  geom_edge_loop(colour='grey') +
  #Color nodes is thegender (as based on male)
  #Shape made by religion
  geom_node_point(aes(color = as.factor(male),shape=Religion), size=6) +
  theme_graph(foreground = 'steelblue', fg_text_colour = 'white') +
  labs(title='A 7th Grade Classroom: Negative Ties') +
  scale_color_manual(
    values = c("0" = "goldenrod1", "1" = "mediumpurple1"), 
    breaks = c("0", "1"),
    labels = c("Female", "Male"),
    name = "Gender"
  )+
  #scale_color_discrete(breaks=c(0,1),labels=c("Female","Male"), name='Gender')+
  theme(text=element_text(family="Calibri"))


ggraph::ggraph(graph2neg, layout = 'kk') + 
  geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm'), colour = 'grey') + 
  geom_edge_loop(colour = 'grey') +
  geom_node_point(aes(color = Religion, shape = as.factor(male)), size = 6) +
  theme_graph(foreground = 'steelblue', fg_text_colour = 'white') +
  labs(title = 'A 7th Grade Classroom: Negative Ties') +
  scale_color_manual(
    values = c(
      "Hindu" = "tomato",
      "Muslim" = "deepskyblue",
      "Other / Unknown" = "gray70"
    ),
    name = "Religion"
  ) +
  scale_shape_manual(
    values = c("0" = 16, "1" = 17),
    labels = c("Female", "Male"),
    name = "Gender"
  ) +
  theme(text = element_text(family = "Calibri"))

#Reciprocity of the graph (proportion of mutual edges, I nominate you, you nominate me)
reciprocity(graph2neg) # 0.1
```

###### One Grade 9 Classroom {.tabset}

```{r, warning=FALSE}
library(dplyr)
library(igraph)
library(ggraph)
#Selects the classroom
graph3neg <- allgraphsNeg[[13]]


graph3neg <- graph3neg %>%
# adds or updates a vertex attribute called "Religion" based on "hindu" attribute
  ## For each vertex -- if Hindu is NA -- Other/Unknown, 1 -- Hindu, Otherwise -- Muslim
  igraph::set_vertex_attr(
    "Religion",
    index = V(graph3neg), # all vertices of graph3neg
    ifelse(
        is.na(vertex_attr(graph3neg)$hindu),'Other / Unknown',
        ifelse(vertex_attr(graph3neg)$hindu==1,'Hindu','Muslim')))

# Create a graph using the Kamada-Kawai (kk) layout
ggraph::ggraph(graph3neg, layout = 'kk') + 
  #Draw edges with arrows
  geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm'), colour='grey') + 
  geom_edge_loop(colour='grey') +
  #Color nodes is thegender (as based on male)
  #Shape made by religion
  geom_node_point(aes(color = as.factor(male),shape=Religion), size=6) +
  theme_graph(foreground = 'steelblue', fg_text_colour = 'white') +
  labs(title='A 9th Grade Classroom: Negative Ties') +
  scale_color_manual(
    values = c("0" = "goldenrod1", "1" = "mediumpurple1"), 
    breaks = c("0", "1"),
    labels = c("Female", "Male"),
    name = "Gender"
  )+
  #scale_color_discrete(breaks=c(0,1),labels=c("Female","Male"), name='Gender')+
  theme(text=element_text(family="Calibri"))

ggraph::ggraph(graph3neg, layout = 'kk') + 
  geom_edge_link(arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm'), colour = 'grey') + 
  geom_edge_loop(colour = 'grey') +
  geom_node_point(aes(color = Religion, shape = as.factor(male)), size = 6) +
  theme_graph(foreground = 'steelblue', fg_text_colour = 'white') +
  labs(title = 'A 9th Grade Classroom: Negative Ties') +
  scale_color_manual(
    values = c(
      "Hindu" = "tomato",
      "Muslim" = "deepskyblue",
      "Other / Unknown" = "gray70"
    ),
    name = "Religion"
  ) +
  scale_shape_manual(
    values = c("0" = 16, "1" = 17),
    labels = c("Female", "Male"),
    name = "Gender"
  ) +
  theme(text = element_text(family = "Calibri"))


#Reciprocity of the graph (proportion of mutual edges, I nominate you, you nominate me)
reciprocity(graph3neg) # 0.1
```

#### Network-Level stats for each class {.tabset}

It's worth explaining/reminding what each stat represents

* average degree (avgdeg) = how connected, on average, each person is
* in-degrees (indeg)  = # of edges nominating a single node, i.e., popularity
* out-degrees (outdeg) = # of edges coming out of a single node, i.e.,outgoing, friendly
* density (dense) = graph density (how tightly-knit the network is)
* transitivity (trans) = likelihood that one's friends are friends with each other, lots of this means a lot of triadic closure
* betweenness (btween) = how much, for a single person, they are on the shortest path between other nodes, nodes play "bridging roles", e.g., connecting two disparate groups
* path length (pathlng) = path length,(avg number of steps it would take to get from one person to another, smaller means compact network)
* reciprocity (recip) = do you nominate me if I nominate you
* number of vertices (numV) = number of vertices in graph (num of nodes)

##### Positive Ties {.tabset}

###### Basic Tables {.tabset}

```{r, warning=FALSE}
# simple loop to step through graph list and provide graph-level stats

## Empty vectors to hold stats
avgdeg <- rep(NA,length(allgraphs)) # vector for mean degree (how connected on average, each person is)
degsd <- rep(NA,length(allgraphs))  # vector of SD of degree
indegsd <- rep(NA,length(allgraphs))  # SD of in-degree (# of edges nominating a single node, i.e., popularity)
outdegsd <- rep(NA,length(allgraphs))  # SD of out-degree (# of edges coming out of a single node, i.e.,outgoing, friendly)
dense <- rep(NA,length(allgraphs))  # vector for graph density (how tightly-knit the network is)
trans <- rep(NA,length(allgraphs))  # vector for graph transitivity (likelihood that one's friends are friends with each other, lots of this means a lot of triadic closure)
btween <- rep(NA,length(allgraphs))  # vector for graph betweeness, (how much, for a single person, they are on the shortest path between other nodes, nodes play "bridging roles", e.g., connecting two disparate groups)
pathlng <- rep(NA,length(allgraphs))  # path length,(avg number of steps it would take to get from one person to another, smaller means compact network)
recip <- rep(NA,length(allgraphs))  # reciprocity (do you nominate me if I nominate you)
numV <- rep(NA,length(allgraphs))   # number of vertices in graph (num of nodes)
# iqvHindu <- rep(NA,length(allgraphs))  # iqv for religious assortment, treating other as NA
# iqvMale <- rep(NA,length(allgraphs))  # iqv for gender assortment

# need to run iqv function if adding those stats
#Loop for functions
for (i in 1:length(allgraphs)){
  avgdeg[i] <- mean(degree(allgraphs[[i]]))
  degsd[i] <- sd(degree(allgraphs[[i]]))
  indegsd[i] <- sd(degree(allgraphs[[i]],mode='in'))
  outdegsd[i] <- sd(degree(allgraphs[[i]],mode='out'))
  dense[i] <- edge_density(allgraphs[[i]])
  trans[i] <- transitivity(allgraphs[[i]])
  btween[i] <- mean(betweenness(allgraphs[[i]]))
  pathlng[i] <- mean_distance(allgraphs[[i]])
  recip[i] <- reciprocity(allgraphs[[i]])
  numV[i] <- length(unique(V(allgraphs[[i]])))  # need to confirm this is calculating full graph size as I want it to
  # iqvMale[i] <- mean(get_iqvs(allgraphs[[i]],'male'),na.rm=T)
  # iqvHindu[i] <- mean(get_iqvs(allgraphs[[i]],'hindu'),na.rm=T)
}

#vector of class names/identifiers
names <- c('A3','B3','C3','A4','B4','C4','A5','B5','C5','A6','B6','C6','A7','B7','C7','A8','B8','C8','A9','B9','C9','A10')
#everything into one
graphstats <- data.frame(ID=names,avgdeg=avgdeg,degsd=degsd,indegsd=indegsd,outdegsd=outdegsd,dense=dense,trans=trans,btween=btween,pathlng=pathlng,recip=recip,numV=numV)
#Grade column
graphstats$grade=as.numeric(substr(graphstats$ID,2,3))  # pull grade number (02--09)

```

```{r, warning=FALSE}
# produce grade-level graphstats via a simple average of the three grades that contribute to it
gradegraphstats <- graphstats %>%
  group_by(grade) %>%
  dplyr::summarise(avgdeg=mean(avgdeg),
            degsd=mean(degsd),
            indegsd=mean(indegsd),
            outdegsd=mean(outdegsd),
            dense=mean(dense),
            trans=mean(trans),
            btween=mean(btween),
            pathlng=mean(pathlng),
            recip=mean(recip))

library(gt)
gt_table <- gt::gt(gradegraphstats) %>%
  gt::tab_header(
    title = "Class Social Network Summary Table",
    subtitle = "Descriptive social network statistics by class"
  ) %>%
  gt::fmt_number(
    columns = everything(),
    decimals = 2
  ) %>%
  gt::tab_options(
    table.font.names = "Times New Roman",
    table.font.size = 12
  )

print(gt_table)
gt::gtsave(gt_table,filename="GradeSocialNetsSummaryTable.html")

# write table for outputting
# write.table(round(gradegraphstats,3), file = "cleaned data/netGradeStats.txt", sep = ",", quote = FALSE, row.names = F)
```

###### Grade Analyses {.tabset}

```{r, warning=FALSE}
#Old chunk
library(corrr) #Note there are three rs here
## Using the data with the classes (not just grades)
## runs all pairwise comparisons
corrInfoClass <- correlate(graphstats[2:12])
# pulls out grade correlations
focus(corrInfoClass,grade)
```

```{r, warning=FALSE}
# Initialize vectors to store results
vars <- names(graphstats)[!(names(graphstats) %in% c("ID", "grade"))]  # exclude ID and grade
results <- data.frame(
  variable = character(),
  r = numeric(),
  p = numeric(),
  stringsAsFactors = FALSE
)

# Loop through each variable and run cor.test with grade
for (v in vars) {
  test <- cor.test(graphstats$grade, graphstats[[v]], method = "pearson")
  results <- rbind(results, data.frame(
    variable = v,
    r = test$estimate,
    p = test$p.value
  ))
}

# View results
print(results)

## What we see is what's sig is a negative correlation between grade and betweenness. That is, the older the grade, the less there are these distinct separate group with high leverage brokers
```

```{r, warning=FALSE}
# visualize the larger correlations,
P1 <- ggplot(gradegraphstats,aes(x=grade,y=btween)) + 
  geom_point(size=4) + 
  geom_smooth(method='lm') + theme_bw() +
  scale_x_continuous(breaks=seq(3,10,1)) +
  ylab("Betweenness Centrality")+
  ggtitle("Betweenness Centrality (p=0.02)")
P2 <- ggplot(gradegraphstats,aes(x=grade,y=recip)) + 
  geom_point(size=4) + 
  geom_smooth(method='lm') + theme_bw() +
  scale_x_continuous(breaks=seq(3,10,1)) +
  ylab("Reciprocity")+
  ggtitle("Reciprocity (p=0.20)")

P3 <- ggplot(gradegraphstats,aes(x=grade,y=trans)) + 
  geom_point(size=4) + 
  geom_smooth(method='lm') + theme_bw() +
  scale_x_continuous(breaks=seq(3,10,1)) +
  ylab("Transitivity")+
  ggtitle("Transivity (p=0.29)")


P4 <- ggplot(gradegraphstats,aes(x=grade,y=dense)) + 
  geom_point(size=4) + 
  geom_smooth(method='lm') + theme_bw() +
  scale_x_continuous(breaks=seq(3,10,1)) +
  ylab("Density")+
  ggtitle("Density (p=0.27)")

library(gridExtra)
grid.arrange(P1, P2, P3, P4, ncol=2,nrow = 2)
```


##### Negative Ties {.tabset}

###### Basic Tables {.tabset}

```{r, warning=FALSE}
# simple loop to step through graph list and provide graph-level stats
avgdeg <- rep(NA,length(allgraphsNeg)) # vector for mean degree
degsd <- rep(NA,length(allgraphsNeg))  # vector of SD of degree
indegsd <- rep(NA,length(allgraphsNeg))  # SD of in-degree
outdegsd <- rep(NA,length(allgraphsNeg))  # SD of out-degree
dense <- rep(NA,length(allgraphsNeg))  # vector for graph density
trans <- rep(NA,length(allgraphsNeg))  # vector for graph transitivty
btween <- rep(NA,length(allgraphsNeg))  # vector for graph betweenenss,
pathlng <- rep(NA,length(allgraphsNeg))  # path length, 
recip <- rep(NA,length(allgraphsNeg))  # reciprocity
numV <- rep(NA,length(allgraphsNeg))   # number of vertices in graph

# need to run iqv function if adding those stats
for (i in 1:length(allgraphsNeg)){
  avgdeg[i] <- mean(degree(allgraphsNeg[[i]]))
  degsd[i] <- sd(degree(allgraphsNeg[[i]]))
  indegsd[i] <- sd(degree(allgraphsNeg[[i]],mode='in'))
  outdegsd[i] <- sd(degree(allgraphsNeg[[i]],mode='out'))
  dense[i] <- edge_density(allgraphsNeg[[i]])
  trans[i] <- transitivity(allgraphsNeg[[i]])
  btween[i] <- mean(betweenness(allgraphsNeg[[i]]))
  pathlng[i] <- mean_distance(allgraphsNeg[[i]])
  recip[i] <- reciprocity(allgraphsNeg[[i]])
  numV[i] <- length(unique(V(allgraphsNeg[[i]])))  # need to confirm this is calculating full graph size as I want it to
}

names <- c('A5','B5','C5','A6','B6','C6','A7','B7','C7','A8','B8','C8','A9','B9','C9','A10')
graphstatsNeg <- data.frame(ID=names,avgdeg=avgdeg,degsd=degsd,indegsd=indegsd,outdegsd=outdegsd,dense=dense,trans=trans,btween=btween,pathlng=pathlng,recip=recip,numV=numV)
graphstatsNeg$grade=as.numeric(substr(graphstatsNeg$ID,2,3))  # pull grade number (02--09)

```

```{r, warning=FALSE}
# produce grade-level graphstats via a simple average of the three grades that contribute to it
gradegraphstatsNeg <- graphstatsNeg %>%
  group_by(grade) %>%
  dplyr::summarise(avgdeg=mean(avgdeg),
            degsd=mean(degsd),
            indegsd=mean(indegsd),
            outdegsd=mean(outdegsd),
            dense=mean(dense),
            trans=mean(trans),
            btween=mean(btween),
            pathlng=mean(pathlng),
            recip=mean(recip))

library(gt)
gt_table <- gt::gt(gradegraphstatsNeg) %>%
  gt::tab_header(
    title = "Class Social Network Negative Ties Summary Table",
    subtitle = "Descriptive social network statistics by class"
  ) %>%
  gt::fmt_number(
    columns = everything(),
    decimals = 2
  ) %>%
  gt::tab_options(
    table.font.names = "Times New Roman",
    table.font.size = 12
  )

print(gt_table)
gt::gtsave(gt_table,filename="GradeNegSocialNetsSummaryTable.html")

# write table for outputting
#write.table(round(gradegraphstatsNeg,3), file = "cleaned data/netGradeStatsNeg.txt", sep = ",", quote = FALSE, row.names = F)

```

###### Grade Analyses {.tabset}

```{r, warning=FALSE}
##Old chunk
# look at grade trends: negative ties
#corrInfo <- correlate(gradegraphstatsNeg)
#focus(corrInfo,grade)
# (not completely sure why run the grade level stats when we have class level)

corrInfoClass <- correlate(graphstatsNeg[2:12])
focus(corrInfoClass,grade)
```

```{r, warning=FALSE}
# Initialize vectors to store results
vars <- names(graphstatsNeg)[!(names(graphstatsNeg) %in% c("ID", "grade"))]  # exclude ID and grade
results <- data.frame(
  variable = character(),
  r = numeric(),
  p = numeric(),
  stringsAsFactors = FALSE
)

# Loop through each variable and run cor.test with grade
for (v in vars) {
  test <- cor.test(graphstatsNeg$grade, graphstatsNeg[[v]], method = "pearson")
  results <- rbind(results, data.frame(
    variable = v,
    r = test$estimate,
    p = test$p.value
  ))
}

# View results
print(results)

## Nothing is significant here, the closest is reciprocity
```

#### Histograms for Point Demonstration {.tabset}

```{r}
p1<-ggplot(propBoth, aes(x = pctOG)) +
  geom_histogram(color = "black", fill = "gray80", bins = 15) +
  xlab("Proportion of Own-Gender Positive Ties")+
  theme_minimal()

p2<-ggplot(propBoth, aes(x = pctOR)) +
  geom_histogram(color = "black", fill = "gray80", bins = 15) +
  xlab("Proportion of Own-Religion Positive Ties")+
  theme_minimal()

p3<-ggplot(propBoth, aes(x = pctOGneg)) +
  geom_histogram(color = "black", fill = "gray80", bins = 15) +
  xlab("Proportion of Own-Gender Negative Ties")+
  theme_minimal()

p4<-ggplot(propBoth, aes(x = pctORneg)) +
  geom_histogram(color = "black", fill = "gray80", bins = 15) +
  xlab("Proportion of Own-Religion Negative Ties")+
  theme_minimal()

#(p1 | p2) / (p3 | p4) +
#  plot_annotation(title = "Histograms of Homophily by Religion and Valence") &
#  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"))

```

```{r}
library(ggplot2)
library(patchwork)
library(scales)

p1 <- ggplot(propBoth, aes(x = pctOG)) +
  geom_histogram(aes(y = ..count../sum(..count..)), 
                 color = "black", fill = "gray80", bins = 15) +
  xlab("% of Own-Gender Friendships") +
  ylab("% of Total Ties") +
  theme_minimal()+
  coord_cartesian(ylim=c(0,0.8))+
  theme(
    axis.title.y = element_blank())+
  scale_x_continuous(labels = percent_format(accuracy = 1))


p2 <- ggplot(propBoth, aes(x = pctOR)) +
  geom_histogram(aes(y = ..count../sum(..count..)), 
                 color = "black", fill = "gray80", bins = 15) +
  xlab("% of Own-Religion Friendships") +
  ylab("% of Participants") +
  theme_minimal()+
  coord_cartesian(ylim=c(0,0.8))+
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank())+
  scale_x_continuous(labels = percent_format(accuracy = 1))



p3 <- ggplot(propBoth, aes(x = pctOGneg)) +
  geom_histogram(aes(y = ..count../sum(..count..)), 
                 color = "black", fill = "gray80", bins = 15) +
  xlab("% of Own-Gender Avoidance") +
  ylab("% of Participants") +
  theme_minimal()+
  coord_cartesian(ylim=c(0,0.8))+
  theme(
    axis.title.y = element_blank())+
  scale_x_continuous(labels = percent_format(accuracy = 1))


p4 <- ggplot(propBoth, aes(x = pctORneg)) +
  geom_histogram(aes(y = ..count../sum(..count..)), 
                 color = "black", fill = "gray80", bins = 15) +
  xlab("% of Own-Religion Avoidance") +
  ylab("% of Participants") +
  theme_minimal()+
  coord_cartesian(ylim=c(0,0.8))+
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank())+
  scale_x_continuous(labels = percent_format(accuracy = 1))



combined_plot_hist<-(p1 | p2) / (p3 | p4) +
  plot_annotation(title = "Histograms of Homophily by Religion and Valence") &
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"))

y_label_plot <- ggplot() +
  theme_void() +
  annotation_custom(
    grob = textGrob("Percentage of Participants", rot = 90, gp = gpar(fontsize = 12))
  )+  
  theme(plot.margin = margin(0, 0, 0, 0))  # remove extra whitespace


combined_final <- (y_label_plot + combined_plot_hist) + 
  plot_layout(widths = c(0.07, 1))+  # left label narrow, main plot wide
  plot_annotation(
    title = "Distributions of Own-Gender and Own-Religion Friendship and Avoidance",
    theme = theme(
      plot.title = element_text(size = 14, face = "bold", hjust = 0.55)))
    
print(combined_final)


# Counting Things
# How many complete other religion avoidance is there
sum(propBoth$pctORneg==0, na.rm=TRUE)
sum(!is.na(propBoth$pctORneg))
sum(propBoth$pctORneg==0, na.rm=TRUE)/sum(!is.na(propBoth$pctORneg))
sum(propBoth$pctORneg==1, na.rm=TRUE)/sum(!is.na(propBoth$pctORneg))
sum(propBoth$pctORneg==0, na.rm=TRUE)/sum(propBoth$pctORneg!=1,na.rm=TRUE)

(sum(propBoth$pctORneg==1, na.rm=TRUE)+ sum(propBoth$pctORneg==0,na.rm=TRUE))/sum(!is.na(propBoth$pctORneg))

# 26% of participants were exclusively other religion
# 16% exclusively their own religion avoidance
# 43% listed only one kind of group

# How many complete other religion friendship is there
sum(propBoth$pctOR==0, na.rm=TRUE)
sum(!is.na(propBoth$pctOR))
sum(propBoth$pctOR==0, na.rm=TRUE)/sum(!is.na(propBoth$pctOR))
sum(propBoth$pctOR==1, na.rm=TRUE)/sum(!is.na(propBoth$pctOR))
(sum(propBoth$pctOR==1, na.rm=TRUE)+ sum(propBoth$pctOR==0,na.rm=TRUE))/sum(!is.na(propBoth$pctOR))
# 5% of participants were exclusively other religion
# 29% of participants chose only their religion for friendship

# how about gender avoidance
sum(propBoth$pctOGneg==0, na.rm=TRUE)
sum(!is.na(propBoth$pctOGneg))
sum(propBoth$pctOGneg==0, na.rm=TRUE)/sum(!is.na(propBoth$pctOGneg))
sum(propBoth$pctOGneg==1, na.rm=TRUE)/sum(!is.na(propBoth$pctOGneg))

# 9% of participants were exclusively other gender avoidant

# how about gender friendships
sum(propBoth$pctOG==0, na.rm=TRUE)
sum(!is.na(propBoth$pctOG))
sum(propBoth$pctOG==0, na.rm=TRUE)/sum(!is.na(propBoth$pctOG))

sum(propBoth$pctOGneg==1, na.rm=TRUE)/sum(!is.na(propBoth$pctOGneg))
sd(propBoth$pctOGneg==1, na.rm=TRUE)
# less than 1% of participants were exclusively other gender friendships
# 49% of participants chose to exclusively befriend only their gender

sum(propBoth$pctOGneg!=1, na.rm=TRUE)/sum(!is.na(propBoth$pctOGneg))

```


### Part 3: Predicting Peer Nominations

#### Predicting Own-Gender Ties {.tabset}

##### Null Model {.tabset}

```{r, warning=FALSE}
# null model
Mnull <- glmer(ownGender ~ 1 + (1|Subject.ID) + (1|class), 
              data = mainReg, family="binomial")
summary(Mnull)

```

##### Adding Classroom Factors
```{r}
M01lp <- glmer(ownGender ~ (propMale + propHindu + propOther + classsize + internelEdge) + (1|Subject.ID) + (1|class), 
            data = mainReg, family="binomial")
summary(M01lp)

# rest is residual variance
drop1(M01lp,test="Chisq") # best is a marginal effect of internelEdge #internelEdge has the highest F value, but still has a P of 0.123
anova(Mnull,M01lp)  # suggests vector of controls doesn't add much!
```

###### Final Base Model
```{r}
M12lp <- glmer(ownGender ~ (Gender + gradeCent)+(propMale  + classsize + internelEdge) +
               (1|Subject.ID) + (1|class), data = mainReg, family="binomial", control=glmerControl(optimizer="bobyqa"))

library(broom.mixed)
summary(M12lp)

broom.mixed::tidy(M12lp,effects="fixed",conf.int=TRUE, exponentiate=TRUE)
```
####### (+GenderM, -Grade, -Class Size, -Internal)

###### Final Religion added
```{r}
MbasePlusRelig6 <- glmer(ownGender ~ relig+(Gender +
                                        gradeCent+
                                        propMale  +
                                        classsize +
                                        internelEdge) + 
  (1|Subject.ID) + (1|class), data = filter(mainReg,relig %in% c('Hindu', 'Muslim')), family="binomial", control=glmerControl(optimizer="bobyqa"))
  
library(broom.mixed)
summary(MbasePlusRelig6)

broom.mixed::tidy(MbasePlusRelig6,effects="fixed",conf.int=TRUE, exponentiate=TRUE)
```
#######(+ReligM(m), +GenderM, -Grade, - Class Size, - Internal)

###### Final GenderAttitudes added
```{r}
## Do gender atttiudes predict nominations?
MgendAtt5 <- glmer(ownGender ~ (Gender + gradeCent + propMale + classsize + internelEdge) + 
                    ownGendAdv+
                    ownGendAdv:gradeCent+
                   (1|Subject.ID) + (1|class), data = mainReg, family="binomial", control=glmerControl(optimizer="bobyqa"))

library(broom.mixed)
summary(MgendAtt5)

broom.mixed::tidy(MgendAtt5,effects="fixed",conf.int=TRUE, exponentiate=TRUE)
```
#######(+GenderM, - ClassSize, - Internal, +Bias, +GradeXBias)

###### Group Identification (ns)

```{r}
## Do social identifications predict nominations?
MgendIdent4 <-  glmer(ownGender ~ (Gender + gradeCent + propMale + classsize + internelEdge) + 
                        Identification_School+
                        Identification_Gender+
                   (1|Subject.ID) + (1|class), data = mainReg, family="binomial", control=glmerControl(optimizer="bobyqa"))
summary(MgendIdent4)
```

###### Final School Norms added

```{r}
MgendNorms3 <- glmer(ownGender ~ (Gender + gradeCent + propMale + classsize + internelEdge) + 
                    SchoolHarmony_BoyGirl + 
                    SchoolHarmony_People  + gradeCent:SchoolHarmony_People + 
                    (1|Subject.ID) + (1|class), data = mainReg, family="binomial", control=glmerControl(optimizer="bobyqa"))
summary(MgendNorms3)
 
library(lme4)

# Model WITHOUT the interaction
MgendNorms_noInt <- glmer(
  ownGender ~ Gender + gradeCent + propMale + classsize + internelEdge +
    SchoolHarmony_BoyGirl + SchoolHarmony_People +
    (1 | Subject.ID) + (1 | class),
  data = mainReg,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa")
)

# Compare models using a likelihood ratio test
anova(MgendNorms_noInt, MgendNorms3, test = "Chisq")

# 1976 vs 1976 without interaction, opting for simpler

summary(MgendNorms_noInt)
```

####### (+GenderM, -Grade, -ClassSize, -Internal, +BoyGirl)

##### Altogether Now

```{r}
PosGenModel<- glmer(ownGender ~ (Gender + gradeCent + propMale + classsize + internelEdge) + 
                       #Bias
                       ownGendAdv+
                       #Bias Grade Interaction
                       ownGendAdv:gradeCent+
                       #SchoolNorms
                       SchoolHarmony_BoyGirl + 
                    (1|Subject.ID) + (1|class), data = mainReg, family="binomial", control=glmerControl(optimizer="bobyqa"))
summary(PosGenModel)

test<- glmer(ownGender ~ (Gender + gradeCent + propMale + classsize + internelEdge) + 
                       #Bias
                       ownGendAdv+
                       #Bias Grade Interaction
                       ownGendAdv:gradeCent+
                       #SchoolNorms
                       SchoolHarmony_BoyGirl + 
                    (1|Subject.ID), data = mainReg, family="binomial", control=glmerControl(optimizer="bobyqa"))
summary(test)
```

#### Predicting Own-Religion Ties {.tabset}

##### Null Model {.tabset}

```{r, warning=FALSE}
# null model
Mnull <- glmer(ownRelig ~ 1 + (1|Subject.ID) + (1|class), 
              data = filter(mainReg, relig %in% c('Hindu', 'Muslim')), family="binomial")
summary(Mnull)
```

##### Adding Classroom Factors
```{r}
M01lp <- glmer(ownRelig ~ (propMale + propHindu + propOther + classsize + internelEdge) + (1|Subject.ID) + (1|class), 
            data = filter(mainReg, relig %in% c('Hindu', 'Muslim')), family="binomial")
summary(M01lp)

# rest is residual variance
drop1(M01lp,test="Chisq") # best is a marginal effect of internelEdge #internelEdge has the highest F value, but still has a P of 0.123
anova(Mnull,M01lp)  # suggests vector of controls doesn't add much!
```

###### Final Base Model

```{r}
M10lp <- glmer(ownRelig ~ (relig + gradeCent)+(propHindu + propOther + classsize + internelEdge) +
               relig:classsize + 
               relig:propHindu + 
               gradeCent:internelEdge +
               relig:gradeCent:classsize+
               (1|Subject.ID) + (1|class), data = filter(mainReg, relig %in% c('Hindu', 'Muslim')), family="binomial", control=glmerControl(optimizer="bobyqa"))

summary(M10lp)
```
#######(-religM, -Grade, +propH(m), -propOther, -MuslimxpropHindu, +gradexinternel, +Muslimxgradexclasssize)

###### Final Gender added
```{r}
# look for interactions w/ religions, noting that this restricts analysis to Hindu and Muslim
MbasePlusGen7 <- glmer(ownRelig ~ Gender*(relig +
                                          propOther+
                                          classsize+
                                          relig:classsize) +
                         internelEdge+
                         gradeCent+
                         propHindu+
                         relig:propHindu+
                         gradeCent:internelEdge+
                         relig:gradeCent:classsize +
  (1|Subject.ID) + (1|class), data = filter(mainReg,relig %in% c('Hindu', 'Muslim')), family="binomial", control=glmerControl(optimizer="bobyqa"))
  
summary(MbasePlusGen7)
```
######## (+GenderM, -religM, +classSize,-Grade,-GenderxPropOther,-GenderxClass,-MuslimxPropHindu,+internalxgrade,+GenderMxMuslimXclass,+Muslimxclassxgrade)

###### Final Religious Attitudes added

```{r}
MReligAtt6 <- glmer(ownRelig ~ (relig + gradeCent)+
               (propHindu + propOther + internelEdge) +
               relig:propHindu + 
               gradeCent:internelEdge +
               ownReligAdv+
               (1|Subject.ID) + (1|class), data = filter(mainReg, relig %in% c('Hindu', 'Muslim')), family="binomial", control=glmerControl(optimizer="bobyqa"))
MReligAtt6 <- update(MReligAtt6, data = model.frame(MReligAtt6))

summary(MReligAtt6)
```
####### (-religM,-grade,+propHindu,-propOther,-internel(m),+bias,+gradeXinternel)

###### Group Identification (ns)

```{r}
MReligIdent9 <- glmer(ownRelig ~(relig + gradeCent)+
               (propHindu + propOther + classsize + internelEdge) +
               relig:propHindu + 
               gradeCent:internelEdge +
               (1|Subject.ID) + (1|class), data = filter(mainReg, relig %in% c('Hindu', 'Muslim')), family="binomial", control=glmerControl(optimizer="bobyqa"))
MReligIdent9 <- update(MReligIdent9, data = model.frame(MReligIdent9))

```

###### Final School Norms added

```{r}
MReligNorms12 <- glmer(ownRelig ~(relig)+
               (propHindu) +
               relig:propHindu + 
                 SchoolHarmony_People+
                 SchoolHarmony_People:relig+
               (1|Subject.ID) + (1|class), data = filter(mainReg, relig %in% c('Hindu', 'Muslim')), family="binomial", control=glmerControl(optimizer="bobyqa"))
MReligNorms12 <- update(MReligNorms12, data = model.frame(MReligNorms12))

summary(MReligNorms12)
```
####### (-religM, -religMxPropHindu, +religMxSchoolHarmony_People)

##### Altogether Now
```{r}
MReligTot <- glmer(ownRelig ~(relig + gradeCent)+
               (propHindu + propOther + classsize + internelEdge) +
               relig:classsize + 
               relig:propHindu + 
               gradeCent:internelEdge +
               relig:gradeCent:classsize+
                 #
                 Gender+
                 SchoolHarmony_People+
                 Gender:propOther+
                 Gender:classsize+
                 Gender:relig:classsize+
                 ownReligAdv+
                 relig:SchoolHarmony_People+
               (1|Subject.ID) + (1|class), data = filter(mainReg, relig %in% c('Hindu', 'Muslim')), family="binomial", control=glmerControl(optimizer="bobyqa"))
summary(MReligTot)

library(emmeans)
emtrends(MReligTot, ~ relig, var = "propHindu")
emtrends(MReligTot, ~ Gender, var="propOther")

test(emtrends(MReligTot, ~ relig, var = "propHindu"))
test(emtrends(MReligTot, ~ Gender, var="propOther"))

```

#### Predicting Own-Gender Negative Ties

##### Null Model {.tabset}

```{r, warning=FALSE}
# null model
Mnull <- glmer(ownGender ~ 1 + (1|Subject.ID) + (1|class), 
              data = mainRegNeg, family="binomial")
summary(Mnull)

```

##### Adding Classroom Factors

###### Final Base Model
```{r}
M15lp <- glmer(ownGender ~ (Gender)+(propMale + propHindu + classsize + internelEdge) +
               (1|Subject.ID) + (1|class), data = mainRegNeg, family="binomial", control=glmerControl(optimizer="bobyqa"))

summary(M15lp)
```
####### (+GenderM, +propHindu, -classize,-internelEdge)

###### Final Religion added

```{r}
MbasePlusReligNeg5<-glmer(ownGender~(Gender + propMale + propHindu + classsize + internelEdge)+
                            relig+
                            relig:propHindu+
               (1|Subject.ID) + (1|class), data = filter(mainRegNeg, relig %in% c('Hindu', 'Muslim')), family="binomial", control=glmerControl(optimizer="bobyqa"))
  
summary(MbasePlusReligNeg5)
```
####### (+GenderM, -classSize, -internelEdge, +propHinduXreligM)

######  Gender Attitudes added

```{r}
MGendAttNeg3 <- glmer(ownGender ~ (Gender)+(propMale + propHindu + classsize + internelEdge) +
                 ownGendAdv+
               (1|Subject.ID) + (1|class), data = mainRegNeg, family="binomial", control=glmerControl(optimizer="bobyqa"))
MGendAttNeg3 <- update(MGendAttNeg3, data = model.frame(MGendAttNeg3))

summary(MGendAttNeg3)
```
####### (+GenderM, +propHindu, -classsize(m), -internelEdges, +ownGendAdv)

######  Group Identification added

```{r}
MGendIdentNeg5 <- glmer(ownGender ~ (Gender)+(propMale + propHindu + classsize + internelEdge) +
                  Identification_Gender+
                  Identification_Gender:Gender+
               (1|Subject.ID) + (1|class), data = mainRegNeg, family="binomial", control=glmerControl(optimizer="bobyqa"))

summary(MGendIdentNeg5)
```
####### (+GenderM, +propHindu, -classSize, -InternelEdge, -GenderIdent, +GenderM:GenderIdent)

###### SchoolNorms (ns)

```{r}
MGendNormsNeg7<- glmer(ownGender ~ (Gender)+(propMale + propHindu + classsize + internelEdge) +
               (1|Subject.ID) + (1|class), data = mainRegNeg, family="binomial", control=glmerControl(optimizer="bobyqa"))
MGendNormsNeg7 <- update(MGendNormsNeg7, data = model.frame(MGendNormsNeg7))
  
```

##### Altogether now
```{r}
MGendNegTot<- glmer(ownGender ~ (Gender)+(propMale + propHindu + classsize + internelEdge) +
                      relig:propHindu+
                      ownGendAdv+
                      Identification_Gender+
                      Identification_Gender:Gender+
               (1|Subject.ID) + (1|class), data = mainRegNeg, family="binomial", control=glmerControl(optimizer="bobyqa"))

summary(MGendNegTot)
```
####### (+GenderM(m), -classsize, -internelEdge,+bias(m), -GenderIdent, +GenderMXGenderIdent)

#### Predicting Own-Relig Negative Ties

##### Null Model {.tabset}

```{r, warning=FALSE}
# null model
Mnull <- glmer(ownRelig ~ 1 + (1|Subject.ID) + (1|class), 
              data = filter(mainRegNeg, relig %in% c('Hindu', 'Muslim')), family="binomial")
summary(Mnull)
```

##### Adding Classroom Factors
```{r}
M01lp <- glmer(ownRelig ~ (propMale + propHindu + propOther + classsize + internelEdge) + (1|Subject.ID) + (1|class), 
            data = filter(mainRegNeg, relig %in% c('Hindu', 'Muslim')), family="binomial")
summary(M01lp)

```

###### Final Base Model

```{r}
M11lp <- glmer(ownRelig ~ relig + 
                gradeCent + 
                propMale + 
                propHindu +
                propOther + 
                classsize + 
                internelEdge +
                relig:propMale + 
                relig:propHindu +
                relig:propOther + 
                relig:classsize +
                relig:internelEdge +
                gradeCent:propOther + 
                (1|Subject.ID) + (1|class), 
             data = filter(mainRegNeg, relig %in% c('Hindu', 'Muslim')), family="binomial", control=glmerControl(optimizer="bobyqa"))

summary(M11lp)
```

####### (-propMale, +propHindu, -classSize, religMxpropMale(m), -religMxpropOther, +religMxclassSize, +religMxinternel, -gradexpropOther)

###### Gender added

```{r}
MReligGend8<- glmer(
  ownRelig ~ Gender + relig + gradeCent + propMale + propHindu + propOther + classsize + internelEdge +
             relig:propMale + relig:propHindu + relig:propOther + relig:classsize + relig:internelEdge + gradeCent:propOther +
             Gender:relig + Gender:propMale + Gender:propHindu + Gender:propOther + Gender:internelEdge +
             Gender:relig:propMale + Gender:relig:propHindu + 
             (1 | Subject.ID) + (1 | class),
  data = filter(mainRegNeg, relig %in% c("Hindu", "Muslim")),
  family = "binomial",
  control = glmerControl(optimizer = "bobyqa")
)


summary(MReligGend8)
```

####### (-GenderM, -propMale, -propHindu, -classsize(m), +religMxpropMale,-religMxpropOther, +religMxclasssize, +religMxinternelEdge ,-gradexpropOther(m), +GenderMxpropMale, +GenderMxpropOther,-GenderMxinternal, -GenderMxReligMxpropMale, -GenderMxReligMxPropHindu)

###### Religious Attitudes added

```{r}
MReligAttNeg5 <- glmer(ownRelig ~ relig + 
                gradeCent + 
                propMale + 
                propHindu +
                propOther + 
                classsize + 
                internelEdge +
                relig:propHindu +
                relig:propOther + 
                relig:classsize +
                relig:internelEdge +
                ownReligAdv+
                (1|Subject.ID) + (1|class), 
             data = filter(mainRegNeg, relig %in% c('Hindu', 'Muslim')), family="binomial", control=glmerControl(optimizer="bobyqa"))
MReligAttNeg5 <- update(MReligAttNeg5, data = model.frame(MReligAttNeg5))

summary(MReligAttNeg5)
```
####### (-grade(m), -propMale, +propHindu, +propOther(m), -classsize, -internelEdge(m), -bias, -religMxpropHindu, religMxclasssize, +religMxinternel)

###### Group Identification (ns)

```{r}
MReligNormsIdent8 <- glmer(ownRelig ~ relig + 
                gradeCent + 
                propMale + 
                propHindu +
                propOther + 
                classsize + 
                internelEdge +
                relig:propHindu +
                relig:propOther + 
                relig:classsize +
                relig:internelEdge +
                gradeCent:propOther + 
                (1|Subject.ID) + (1|class), 
             data = filter(mainRegNeg, relig %in% c('Hindu', 'Muslim')), family="binomial", control=glmerControl(optimizer="bobyqa"))
MReligNormsIdent8 <- update(MReligNormsIdent8, data = model.frame(MReligNormsNeg8))
 
```

###### School Norms added

```{r}
MReligNormsNeg7 <- glmer(ownRelig ~ relig + 
                gradeCent + 
                propMale + 
                propHindu +
                propOther + 
                classsize + 
                internelEdge +
                relig:propHindu +
                relig:propOther + 
                relig:classsize +
                relig:internelEdge +
                gradeCent:propOther + 
                 SchoolHarmony_HinduMuslim+
                (1|Subject.ID) + (1|class), 
             data = filter(mainRegNeg, relig %in% c('Hindu', 'Muslim')), family="binomial", control=glmerControl(optimizer="bobyqa"))
MReligNormsNeg7 <- update(MReligNormsNeg7, data = model.frame(MReligNormsNeg7))

summary(MReligNormsNeg7)
```
####### (-propMale, +propHindu, -classsize, -SchoolHarmony_HinduMuslim(m), -religMxpropHindu, -religMxpropOther, +religMxclasssize, +religMxinternel, -gradexpropOther )

##### Altogether Now
```{r}
MReligNegTot <- glmer(ownRelig ~ relig + 
                gradeCent + 
                propMale + 
                propHindu +
                propOther + 
                classsize + 
                internelEdge +
                relig:propMale + 
                relig:propHindu +
                relig:propOther + 
                relig:classsize +
                relig:internelEdge +
                gradeCent:propOther + 
                  Gender+
                  Gender:propMale+
                  Gender:propOther+
                  Gender:internelEdge+
                  Gender:propMale:relig+
                  Gender:relig:propHindu+
                  ownReligAdv+
                  SchoolHarmony_HinduMuslim+
                (1|Subject.ID) + (1|class), 
             data = filter(mainRegNeg, relig %in% c('Hindu', 'Muslim')), family="binomial", control=glmerControl(optimizer="bobyqa"))
summary(MReligNegTot)
```

```{r}
library(emmeans)

# propMale × religion × gender
emtrends(
  MReligNegTot,
  ~ relig * Gender,
  var = "propMale")

# propHindu × religion × gender
emtrends(
  MReligNegTot,
  ~ relig * Gender,
  var = "propHindu")

# classsize × religion
emtrends(
  MReligNegTot,
  ~ relig,
  var = "classsize")

# propOther × religion × gender
emtrends(
  MReligNegTot,
  ~ relig * Gender,
  var = "propOther")

# internelEdge × religion
emtrends(
  MReligNegTot,
  ~ relig,
  var = "internelEdge")

# internelEdge × gender
emtrends(
  MReligNegTot,
  ~ Gender,
  var = "internelEdge")
```


### SOM: Cross-group Friendships and Crossers

```{r}
# Load SNA packages

library(tidyverse)
library(igraph)
library(sna)

#You're getting warnings, be careful that you make sure to specify package before starting

edges<-mainReg%>%
  filter(!is.na(Response))%>%
  select(class,egoID,Response)%>%
  #mapping EgoID->Subject ID for "from"
  left_join(mainReg%>%select(class,egoID,Subject.ID),by=c("class","egoID"))%>%
  rename(from=Subject.ID)%>%
  #mapping egoID --> Subject.ID for "to"
  left_join(mainReg%>%select(class,egoID,Subject.ID),by=c("class","Response"="egoID"))%>%
  rename(to=Subject.ID)%>%
  distinct(class, from, to, .keep_all = TRUE)

edges <- mainReg %>%
  filter(!is.na(Response)) %>%
  select(class,egoID,Response)%>%
  # Map egoID of nominator to Subject.ID
  left_join(mainReg %>% select(class, egoID, Subject.ID), by = c("class", "egoID")) %>%
  rename(from = Subject.ID) %>%
  # Map Response (class-local) to Subject.ID of nominee
  left_join(mainReg %>% select(class, egoID, Subject.ID), by = c("class", "Response" = "egoID")) %>%
  rename(to = Subject.ID)

# Remove edges where mapping failed (i.e., 4 nominated 6 but 6 didn't participate)
edges <- edges %>% filter(!is.na(from) & !is.na(to))


#This is the alters

nodes<-mainReg%>%
  distinct(Subject.ID, Gender, grade,classroom,class,relig,
           Attitudes_Boys,Attitudes_Girls,Attitudes_Hindus,Attitudes_Muslims,
           Identification_Religion,Identification_Gender,
           Religiosity_Religiosity,
           SchoolHarmony_BoyGirl,SchoolHarmony_HinduMuslim,SchoolHarmony_People,
           Wellbeing_EnoughFriends,Wellbeing_Happy,Wellbeing_Lonely,Wellbeing_OthersMean,
           ownGender,ownRelig,classID,
           propMale,propHindu,propOther,classsize,internelEdge)%>%
  distinct(Subject.ID, .keep_all = TRUE)

```

```{r}
#Pooled Network (means everyone)
library(igraph)
library(dplyr)

# Build pooled network across all classes
g_all <- graph_from_data_frame(
  d = edges %>% select(from, to),
  directed = TRUE
)

# Add node attributes from participants
node_attrs <- mainReg %>%
  distinct(Subject.ID, Gender, grade, classroom, relig,class) %>%
  rename(node = Subject.ID)

V(g_all)$Gender <- node_attrs$Gender[match(V(g_all)$name, node_attrs$node)]
V(g_all)$grade <- node_attrs$grade[match(V(g_all)$name, node_attrs$node)]
V(g_all)$classroom <- node_attrs$classroom[match(V(g_all)$name, node_attrs$node)]
V(g_all)$relig <- node_attrs$relig[match(V(g_all)$name, node_attrs$node)]

vcount(g_all) # total nodes
ecount(g_all) # total edges

igraph::edge_density(g_all)

reciprocity(g_all)

```

```{r}
# Build per-class binary networks
# Split edges by class
edges_by_class <- edges %>% group_by(class) %>% group_split()

graphs <- lapply(edges_by_class, function(df_class) {
  g <- graph_from_data_frame(
    d = df_class %>% select(from, to),
    directed = TRUE
  )
  
  # Add node attributes for that class
  nodes_class <- mainReg %>%
    filter(class == df_class$class[1]) %>%
    distinct(Subject.ID, Gender, grade, classroom, relig,class) %>%
    rename(node = Subject.ID)
  
  V(g)$Gender <- nodes_class$Gender[match(V(g)$name, nodes_class$node)]
  V(g)$grade <- nodes_class$grade[match(V(g)$name, nodes_class$node)]
  V(g)$classroom <- nodes_class$classroom[match(V(g)$name, nodes_class$node)]
  V(g)$relig <- nodes_class$relig[match(V(g)$name, nodes_class$node)]
  
  return(g)
})

# Name the list by class
names(graphs) <- sapply(edges_by_class, function(x) unique(x$class))

```

```{r }
#Creating Node Summaries
ego_summary<-propTies%>%
  mutate(propOtherGender=1-pctOG,
         propOtherRelig=1-pctOR)%>%
  distinct(Subject.ID, .keep_all=TRUE)

#Drop duplicate info
ego_summary<-ego_summary[,-c(1:3)]

ego_summary<-nodes%>%
  left_join(ego_summary,by="Subject.ID")

```

```{r}
library(dplyr)

# By gender
ego_summary %>%
  group_by(Gender) %>%
  summarise(
    meanCrossGender = mean(propOtherGender, na.rm = TRUE),
    meanCrossRelig = mean(propOtherRelig, na.rm = TRUE),
    n = n()
  )

# By grade
ego_summary %>%
  group_by(grade) %>%
  summarise(
    meanCrossGender = mean(propOtherGender, na.rm = TRUE),
    meanCrossRelig = mean(propOtherRelig, na.rm = TRUE)
  )

```

```{r}
library(ggplot2)

# Boxplot of cross-religion nominations by grade
ggplot(ego_summary, aes(x = factor(grade), y = propOtherRelig)) +
  geom_boxplot() +
  labs(x = "Grade", y = "Proportion of cross-religion nominations") +
  theme_minimal()

# Cross-gender nominations by gender
ggplot(ego_summary, aes(x = Gender, y = propOtherGender)) +
  geom_boxplot() +
  labs(y = "Proportion of cross-gender nominations") +
  theme_minimal()

```
## Predicting crossing gender or religious lines {.tabset}

### Linear Regression {.tabset}

```{r}
ego_summary_filtered <- ego_summary %>%
  filter(relig %in% c("Hindu", "Muslim"))

# Cross-gender nominations
lm_crossGender <- lm(propOtherGender ~ Gender + grade + relig, data = ego_summary_filtered)
summary(lm_crossGender)


# Cross-religion nominations predicted by grade and gender
lm_crossRelig <- lm(propOtherRelig ~ Gender + grade + relig, data = ego_summary_filtered)
summary(lm_crossRelig)

```

## Summaries of the High Noms. 
```{r}
# Figuring out quartiles
ego_summary_filtered <- ego_summary_filtered %>%
  mutate(
    high_crossRelig = propOtherRelig >= quantile(propOtherRelig, 0.75, na.rm = TRUE),
    high_crossGender = propOtherGender > 0
  )

#So note, we have a lot more diversity on other relig than other gender, 

# Numeric summaries
summary_high_relig <- ego_summary_filtered %>%
  filter(high_crossRelig) %>%
  summarise(
    mean_grade = mean(grade, na.rm = TRUE),
    prop_male = mean(Gender == "M", na.rm = TRUE),
    mean_religiosity = mean(Religiosity_Religiosity, na.rm = TRUE),
    mean_SES = mean(SESLadder_SESLadder, na.rm = TRUE)
  )

summary_high_gender <- ego_summary_filtered %>%
  filter(high_crossGender) %>%
  summarise(
    mean_grade = mean(grade, na.rm = TRUE),
    prop_male = mean(Gender == "M", na.rm = TRUE),
    mean_religiosity = mean(Religiosity_Religiosity, na.rm = TRUE),
    mean_SES = mean(SESLadder_SESLadder, na.rm = TRUE)
  )

print(summary_high_relig)
print(summary_high_gender)
```

### Tests of High vs. Low nominators {.tabset}

```{r}

# T-tests for numeric variables
t.test(grade ~ high_crossRelig, data = ego_summary_filtered)
t.test(Religiosity_Religiosity ~ high_crossRelig, data = ego_summary_filtered)
t.test(grade ~ high_crossGender, data = ego_summary_filtered)
t.test(Religiosity_Religiosity ~ high_crossGender, data = ego_summary_filtered)


# Chi-squared for categorical variables
chisq.test(table(ego_summary_filtered$Gender, ego_summary_filtered$high_crossRelig))
chisq.test(table(ego_summary_filtered$relig, ego_summary_filtered$high_crossRelig))

chisq.test(table(ego_summary_filtered$Gender, ego_summary_filtered$high_crossGender))
chisq.test(table(ego_summary_filtered$relig, ego_summary_filtered$high_crossGender))
```


# Create SNA values
```{r}

library(dplyr)
library(igraph)

graphs <- lapply(names(graphs), function(class_name) {
  g <- graphs[[class_name]]
  
  # Degree metrics
  V(g)$indegree  <- igraph::degree(g, mode = "in")
  V(g)$outdegree <- igraph::degree(g, mode = "out")
  V(g)$degree    <- igraph::degree(g, mode = "all")
  
  # Betweenness centrality
  V(g)$betweenness <- igraph::betweenness(g, directed = TRUE)
  
  #Closeness
  V(g)$closeness <-igraph::closeness(g,mode="all",normalized=TRUE)
  
  
  # Filter edges for this class
  edges_class <- edges %>% dplyr::filter(class == class_name)
  
  return(g)
})
# Keep names intact
names(graphs) <- sapply(edges_by_class, function(df_class) unique(df_class$class))


class_metrics <- lapply(names(graphs), function(class_name) {
  g <- graphs[[class_name]]
  data.frame(
    class = class_name,
    density = igraph::edge_density(g),
    transitivity = igraph::transitivity(g, type = "global")
  )
}) %>% bind_rows()

# Merge

library(purrr)
node_data <- imap_dfr(graphs, function(g, class_name) {
  as_data_frame(g, what = "vertices") %>%
    mutate(class = class_name)
})

node_data <- lapply(names(graphs), function(class_name) {
  g <- graphs[[class_name]]
  as_data_frame(g, what = "vertices") %>%
    mutate(class = class_name)
}) %>% bind_rows()

# Now do the join
ego_summary_metrics <- ego_summary_filtered %>%
  left_join(
    node_data %>% select(name, indegree, outdegree, degree, betweenness, closeness, class),
    by = c("Subject.ID" = "name","class"="class")
  )
```

### SNA Predictors of Cross-group friendships {.tabset}

#### Individual Factors {.tabset}

#### Centrality (how influential) {.tabset}

Betweeness - Measures how often a node lies on the shortest paths between other nodes
"brokers", "gatekeepers", "bridges"

Closeness - Average distance from a node to all the others in the network 
"nodes with high can quickly reach others and spread"

Eigenvector - Measures how connected to well-connected nodes they are

Indegree - How popular someone is

##### Betweenness (brokers)

```{r}
# ============================================
# 5. Compare centrality for cross-group kids
# ============================================

# t-test for betweenness
t.test(betweenness ~ high_crossGender, data = ego_summary_metrics)
t.test(betweenness ~ high_crossRelig,  data = ego_summary_metrics)

# So for gender, kids who are high cross group friendship people, tend to be bridge makers, null effect for Religion
```

##### Closeness

```{r}
t.test(closeness ~ high_crossGender, data = ego_summary_metrics)
t.test(closeness ~ high_crossRelig,  data = ego_summary_metrics)

# more closeness for those who cross gender
# ns for those who cross religion
```


##### Indegree & Outdegree

```{r}
# t-test for indegree 
t.test(indegree ~ high_crossGender, data = ego_summary_metrics)
t.test(indegree ~ high_crossRelig,  data = ego_summary_metrics)

# Okay, so interestingly,gender crossers are more popular than others. 
# Religion crossers are less popular than their counterparts

### Note for future self to struggle with, would love to see what kind of indegree we're talking about. Are cross-groupers more popular among people from the other group or their own?
t.test(outdegree ~ high_crossRelig,  data = ego_summary_metrics)
t.test(outdegree ~ high_crossGender, data = ego_summary_metrics)



```
###### By just base ties, not within specific

```{r}
library(dplyr)

# Merge only Subject.ID, high_cross_Gender, high_cross_Relig from ego_summary_metrics
ties2_aug <- ties2 %>%
  left_join(
    ego_summary_metrics %>% select(Subject.ID, high_crossGender, high_crossRelig),
    by = "Subject.ID"
  )

t.test(numAlters ~ high_crossRelig,  data = ties2_aug)
t.test(numAlters ~ high_crossGender, data = ties2_aug)
```

##### Number of Nominations {.tabset}

```{r}
# ============================================
# 7. Are kids who nominate more more likely to have cross-group friendships
# ============================================
# Cross-gender
cor.test(ego_summary$numNom, ego_summary$propOtherGender, use="complete.obs")

# Cross-religion
cor.test(ego_summary$numNom, ego_summary$propOtherRelig, use="complete.obs")

# yes, kids who nominate more are more likely to nominate across other religions and gender
```

Okay, so taken together
* for Gender: Kids who make friends across gender are more popular/recognized by their peers (indegree), serve as bridges between groups (most likely gender clusters), and are generally well connected (they can reach many peers efficiently (shortest paths)), but are not necessarily clustered together in a network. They bridge clusters but they don't have a highly interconnected "core"

* for Religion: Kids who make friends across religious lines are not as popular. They're not more central in any shape or form, neither are they more influential or more connected. 


### Characterizing Cross-Group Friendships {.tabset}

#### Are they more reciprocal? {.tabset}

```{r}

# Assuming ego_summary has Subject.ID, Gender, relig
edges_aug <- edges %>%
  # Add 'from' node info
  left_join(ego_summary %>% select(Subject.ID, Gender, relig),
            by = c("from" = "Subject.ID")) %>%
  rename(fromGender = Gender, fromRelig = relig) %>%
  # Add 'to' node info
  left_join(ego_summary %>% select(Subject.ID, Gender, relig),
            by = c("to" = "Subject.ID")) %>%
  rename(toGender = Gender, toRelig = relig) %>%
  # Create cross-group indicators
  mutate(
    ownGender = ifelse(fromGender == toGender, 1, 0),
    ownRelig  = ifelse(fromRelig == toRelig, 1, 0)
  )


# Function to calculate reciprocity for cross-group ties
calculate_reciprocity <- function(edges_df) {
  
  # Add a 'reciprocated' column
  edges_df <- edges_df %>%
    mutate(reciprocated = mapply(function(f, t) {
      any(edges_df$from == t & edges_df$to == f)
    }, from, to))
  
  # Summarize reciprocity by ownGender
  gender_summary <- edges_df %>%
    group_by(ownGender) %>%
    summarise(
      n_edges = n(),
      prop_reciprocated = mean(reciprocated, na.rm = TRUE)
    )
  
  # Chi-squared test for gender
  table_gender <- table(edges_df$ownGender, edges_df$reciprocated)
  gender_chisq <- chisq.test(table_gender)
  
  # Summarize reciprocity by ownRelig
  relig_summary <- edges_df %>%
    group_by(ownRelig) %>%
    summarise(
      n_edges = n(),
      prop_reciprocated = mean(reciprocated, na.rm = TRUE)
    )
  
  # Chi-squared test for religion
  table_relig <- table(edges_df$ownRelig, edges_df$reciprocated)
  relig_chisq <- chisq.test(table_relig)
  
  # Return everything in a list
  return(list(
    gender_summary = gender_summary,
    gender_chisq = gender_chisq,
    relig_summary = relig_summary,
    relig_chisq = relig_chisq
  ))
}


recip_results <- calculate_reciprocity(edges_aug)

# View summaries
recip_results$gender_summary
recip_results$relig_summary

# View chi-squared tests
recip_results$gender_chisq
recip_results$relig_chisq

# So what we're seeing is that yeah, people are more likely to reciprocate same-group friendships than cross-group friendships
```
#### Reciprocity Compare Across with CIs

```{r}
library(dplyr)
library(purrr)

edges_aug <- edges %>%
  left_join(ego_summary %>% select(Subject.ID, Gender, relig),
            by = c("from" = "Subject.ID")) %>%
  rename(fromGender = Gender, fromRelig = relig) %>%
  
  left_join(ego_summary %>% select(Subject.ID, Gender, relig),
            by = c("to" = "Subject.ID")) %>%
  rename(toGender = Gender, toRelig = relig) %>%
  
  mutate(
    ownGender = ifelse(fromGender == toGender, 1, 0),
    ownRelig  = ifelse(fromRelig == toRelig, 1, 0)
  )


calculate_reciprocity <- function(edges_df) {
  
  # Add reciprocated flag
  edges_df <- edges_df %>%
    mutate(reciprocated = mapply(function(f, t) {
      any(edges_df$from == t & edges_df$to == f)
    }, from, to))
  
  # Helper for CI
  binom_ci <- function(x, n) {
    bt <- binom.test(x, n)
    tibble(
      lower = bt$conf.int[1],
      upper = bt$conf.int[2]
    )
  }
  
 # Gender
  
  gender_summary <- edges_df %>%
    group_by(ownGender) %>%
    summarise(
      n_edges = n(),
      n_recip = sum(reciprocated),
      prop_recip = mean(reciprocated),
      .groups = "drop"
    ) %>%
    rowwise() %>%
    mutate(binom_ci(n_recip, n_edges)) %>%
    ungroup()
  
  gender_chisq <- chisq.test(table(edges_df$ownGender, edges_df$reciprocated))
  
#Religion 
  relig_summary <- edges_df %>%
    group_by(ownRelig) %>%
    summarise(
      n_edges = n(),
      n_recip = sum(reciprocated),
      prop_recip = mean(reciprocated),
      .groups = "drop"
    ) %>%
    rowwise() %>%
    mutate(binom_ci(n_recip, n_edges)) %>%
    ungroup()
  
  relig_chisq <- chisq.test(table(edges_df$ownRelig, edges_df$reciprocated))
  
# Gender vs. Religion
  comparison <- tibble(
    grouping = c("Gender (own vs cross)", "Religion (own vs cross)"),
    chi_sq = c(gender_chisq$statistic, relig_chisq$statistic),
    df = c(gender_chisq$parameter, relig_chisq$parameter),
    p_value = c(gender_chisq$p.value, relig_chisq$p.value)
  )
  
  return(list(
    gender_summary = gender_summary,
    gender_chisq = gender_chisq,
    relig_summary = relig_summary,
    relig_chisq = relig_chisq,
    comparison_table = comparison
  ))
}

recip_results <- calculate_reciprocity(edges_aug)

# View results
recip_results$gender_summary
recip_results$relig_summary
recip_results$comparison_table

# Gender and religion same-group reciprocity
gender_recip <- recip_results$gender_summary %>% filter(ownGender == 1)
relig_recip <- recip_results$relig_summary %>% filter(ownRelig == 1)

prop.test(
  x = c(gender_recip$n_recip, relig_recip$n_recip),
  n = c(gender_recip$n_edges, relig_recip$n_edges)
)

# Gender and religion cross-group reciprocity
gender_recip <- recip_results$gender_summary %>% filter(ownGender == 0)
relig_recip <- recip_results$relig_summary %>% filter(ownRelig == 0)

prop.test(
  x = c(gender_recip$n_recip, relig_recip$n_recip),
  n = c(gender_recip$n_edges, relig_recip$n_edges)
)

```

#### Are they more triadic/clustered? Local Transitivity (individual triadic closure)
```{r}

library(igraph)
library(dplyr)

graphs <- lapply(graphs, function(g) {
  V(g)$local_transitivity <- transitivity(g, type = "local", isolates = "zero")
  return(g)
})


node_data <- lapply(names(graphs), function(class_name) {
  g <- graphs[[class_name]]
  as_data_frame(g, what = "vertices") %>%
    mutate(class = class_name)
}) %>% bind_rows()

# Merge
ego_summary_metric_transitivity <- ego_summary %>%
  left_join(node_data %>% select(name, class, local_transitivity), 
            by = c("Subject.ID" = "name", "class" = "class"))


# Cross-gender
lm_crossGender <- lm(local_transitivity ~ propOtherGender, data = ego_summary_metric_transitivity)
summary(lm_crossGender)

# Children who have higher proportions of other gender friends, have less triadic closure. These groups are lesss "cliquey"

# Cross-religion
lm_crossRelig <- lm(local_transitivity ~ propOtherRelig, data = ego_summary_metric_transitivity)
summary(lm_crossRelig)

# Children who have higher proportions of other religion friends also have less triadic closure

```

## SOM5: Wellbeing

```{r, warning=FALSE}
# convert to long
wellbeingLong <- subjects %>%
  dplyr::select(Subject.ID,grade,Gender,relig,ageinyears,Wellbeing_EnoughFriends:Wellbeing_OthersMean) %>%
  gather(target,rating,Wellbeing_EnoughFriends:Wellbeing_OthersMean) %>%
  mutate(target = substr(target,11,25),
         wellbeing = 6-rating)

table(wellbeingLong$target) #sanity check
```
```{r, warning=FALSE}
library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(grid)  # for unit()

# Define target categories of interest and ensure factor order
targets_of_interest <- c('EnoughFriends', 'Happy', 'Lonely', 'OthersMean',
                         'RichPoor')
target_colors <- brewer.pal(n = length(targets_of_interest), name = "Set2")
names(target_colors) <- targets_of_interest  # name them so it's clear

wellbeingLong <- wellbeingLong %>%
  filter(target %in% targets_of_interest) %>%
  mutate(targetF = factor(target, levels = targets_of_interest))

# Compute means for labeling
mean_labels <- wellbeingLong %>%
  group_by(target) %>%
  dplyr::summarise(mean_wellbeing = mean(wellbeing, na.rm = TRUE)) %>%
  mutate(label_y = mean_wellbeing + 0.2)  # optional nudge upward

# Create the plot
combined_plot<-ggplot(wellbeingLong, aes(x = target, y = wellbeing, color = target)) +
  geom_jitter(width = 0.05, height = 0.15, size = 3, alpha = 0.6) +  # colored dots
  geom_violin(color = "black", fill = NA, linewidth = 0.5, width = 0.5) +  # transparent violin
  geom_boxplot(color = "black", fill = NA, width = 0.4, outlier.shape = NA) +  # boxplot
  stat_summary(fun = mean, geom = "point", shape = 18, size = 3, color = "darkred") +  # red mean point
  geom_label(
    data = mean_labels,
    aes(x = target, y = mean_wellbeing, label = round(mean_wellbeing, 2)),
    inherit.aes = FALSE,
    nudge_x = 0.25,
    size = 3,
    fill = "white",
    color = "black",
    label.size = 0.25,
    label.r = unit(0.15, "lines")
  ) +
  scale_color_manual(values = target_colors) +
  scale_y_continuous(breaks = seq(1, 5, 1), limits = c(1, 5.5)) +
  theme_bw() +
  xlab("Feeling") +
  ylab(" Agreement \n (1=Definitely disagree; 5 = Definitely agree)") +
  ggtitle("Wellbeing") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
  )

# Show
print(combined_plot)

ggsave("combined_plot_wellbeing.png",combined_plot,width=5.5,height=6,dpi=300)

```


### Age differences {.tabset}

#### EnoughFriends {.tabset}

```{r, warning=FALSE}
cor.test(subjects$Wellbeing_EnoughFriends,subjects$ageinyears)
# -0.035, p=0.23
```

#### Happy {.tabset}

```{r, warning=FALSE}
cor.test(subjects$Wellbeing_Happy,subjects$ageinyears)
# -0.187, p<0.001
# older, more happy
```

#### Lonely {.tabset}

```{r, warning=FALSE}
cor.test(subjects$Wellbeing_Lonely,subjects$ageinyears)
# 0.24, p<0.001
#older, less lonely
```

#### OthersMean {.tabset}

```{r, warning=FALSE}
cor.test(subjects$Wellbeing_OthersMean,subjects$ageinyears)
# -0.12, p<0.001
#older, others are more mean
```

### Gender differences {.tabset}

```{r, warning=FALSE}
# by gender - not too much going on
wbPlotGender <- ggplot(filter(wellbeingLong,!is.na(Gender)),aes(x=target,y=wellbeing,group=Gender,fill=Gender))
wbPlotGender + stat_summary(fun.y=mean, geom="bar", size=2,position = position_dodge()) +
  stat_summary(fun.data="mean_cl_boot", geom="linerange",position = position_dodge(.9)) +
  scale_y_continuous(breaks=seq(1,5,1)) +  coord_cartesian(ylim=c(1,5)) +
  theme_bw() + xlab("Norm Type") + ylab("Endorsement of Positive Norm")
```
#### Do they Exist? (No) {.tabset} 

```{r, warning=FALSE}
#ANOVAs to test: 

# nest by targets (which will be the outcomes of subsequent analyses)
nested <- wellbeingLong %>% 
  filter(!is.na(Gender)) %>%
  group_by(target) %>%
  nest()

# run the anova on each data frame (the data in the 3rd column)
# map takes the data column, runs the analysis on the right, and saves results in the
# new column created by mutate
nested <- nested %>%
  mutate(model = map(data, ~aov(wellbeing ~ Gender, data = .)))

# this creates a new column which is a dataframe of all the anova output
# nicely tidied up so you get the test statistics for each term
nested <- nested %>%
  mutate(tidy = map(model, broom::tidy))

#Here are the results
nested %>%
  unnest(tidy)

tab1 <- process_nested(nested,"nested1")

# Print the combined results table to view all ANOVA summaries 
print(tab1)

library(dplyr)
library(gt)

tab1_color<-tab1 %>%
  mutate(
    Gender.p.value = signif(Gender.p.value, 2)
  ) %>%
  gt() %>%
  fmt_number(
    columns = c("Gender.F", "Gender.p.value"),
    decimals = 2
  ) %>%
  data_color(
    columns = "Gender.p.value",
    colors = scales::col_bin(
      bins = c(-Inf, 0.05, Inf),
      palette = c("red", "black")
    )
  ) %>%
  cols_label(
    target = "Target",
    Gender.F = "F Statistic",
    Gender.p.value = "p-value"
  ) %>%
  tab_options(
    table.font.size=px(10)
  )

print(tab1_color)
```
### Religious differences {.tabset}

```{r, warning=FALSE}
# by religion - suggests bigger diffs here!
wbPlotRelig <- ggplot(filter(wellbeingLong,relig %in% c('Hindu','Muslim')),aes(x=target,y=wellbeing,group=relig,fill=relig))
wbPlotRelig + stat_summary(fun.y=mean, geom="bar", size=2,position = position_dodge()) +
  stat_summary(fun.data="mean_cl_boot", geom="linerange",position = position_dodge(.9)) +
  scale_y_continuous(breaks=seq(1,5,1)) +  coord_cartesian(ylim=c(1,5)) +
  theme_bw() + xlab("Norm Type") + ylab("Endorsement of Positive Norm")
```

#### Do they Exist? {.tabset}

```{r, warning=FALSE}
#ANOVAs to test: 

# nest by targets (which will be the outcomes of subsequent analyses)
nested <- wellbeingLong %>% 
  filter(relig %in% c('Hindu','Muslim')) %>%
  group_by(target) %>%
  nest()

# run the anova on each data frame (the data in the 3rd column)
# map takes the data column, runs the analysis on the right, and saves results in the
# new column created by mutate
nested <- nested %>%
  mutate(model = map(data, ~aov(wellbeing ~ relig, data = .)))

# this creates a new column which is a dataframe of all the anova output
# nicely tidied up so you get the test statistics for each term
nested <- nested %>%
  mutate(tidy = map(model, broom::tidy))

#Here are the results
nested %>%
  unnest(tidy)

tab1 <- process_nested(nested,"nested1")

# Print the combined results table to view all ANOVA summaries 
print(tab1)

library(dplyr)
library(gt)

tab1_color<-tab1 %>%
  mutate(
    relig.p.value = signif(relig.p.value, 2)
  ) %>%
  gt() %>%
  fmt_number(
    columns = c("relig.F", "relig.p.value"),
    decimals = 2
  ) %>%
  data_color(
    columns = "relig.p.value",
    colors = scales::col_bin(
      bins = c(-Inf, 0.05, Inf),
      palette = c("red", "black")
    )
  ) %>%
  cols_label(
    target = "Target",
    relig.F = "F Statistic",
    relig.p.value = "p-value"
  ) %>%
  tab_options(
    table.font.size=px(10)
  )
print(tab1_color)
```
#### Direction? {.tabset}

##### EnoughFriends {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$Wellbeing_EnoughFriends~onlyMH$relig) # H < M, p=0.025
effsize::cohen.d(onlyMH$Wellbeing_EnoughFriends~onlyMH$relig) #d=-0.13
#Hindus felt that they had enough friends more
```

##### Happy {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$Wellbeing_Happy~onlyMH$relig) # H < M, p=0.033
effsize::cohen.d(onlyMH$Wellbeing_Happy~onlyMH$relig) #d=-0.13
#Hindus reported being happy more than Muslims
```


## SOM6: Religious Observance

```{r, warning=FALSE}
# convert to long
religLong <- subjects %>%
  dplyr::select(Subject.ID,grade,Gender,relig,ageinyears,Religiosity_Religiosity,ReligFreq_Celebrate:ReligFreq_ReligiousPlace) %>%
  gather(target,rating,Religiosity_Religiosity,ReligFreq_Celebrate:ReligFreq_ReligiousPlace) %>%
  mutate(target = substr(target,11,25),
         religion = ifelse(target=='y_Religiosity',5-rating,6-rating))

table(religLong$target) #sanity check

religLong %>%
  group_by(target) %>%
  dplyr::summarise(avg = mean(religion,na.rm=T),
            std = sd(religion,na.rm=T))
```
### Age differences {.tabset}

#### Celebrate {.tabset}

```{r, warning=FALSE}
cor.test(subjects$ReligFreq_Celebrate,subjects$ageinyears)
# -0.016, p=0.589
```
#### Pray {.tabset}

```{r, warning=FALSE}
cor.test(subjects$ReligFreq_Pray,subjects$ageinyears)
# -0.12, p<0.589
# More praying with age
```

#### Read {.tabset}

```{r, warning=FALSE}
cor.test(subjects$ReligFreq_Read,subjects$ageinyears)
# .11, p<0.001
#less reading with age
```
#### ReligiousPlaces {.tabset}

```{r, warning=FALSE}
cor.test(subjects$ReligFreq_ReligiousPlace,subjects$ageinyears)
# -0.03, p=0.38
```
#### Religiosity {.tabset}

```{r, warning=FALSE}
cor.test(subjects$Religiosity_Religiosity,subjects$ageinyears)
# 0.33, p<0.001
#less religious with age
```

###Gender differences {.tabset}

#### Do they Exist? {.tabset} 

```{r, warning=FALSE}
#ANOVAs to test: 

# nest by targets (which will be the outcomes of subsequent analyses)
nested <- religLong %>% 
  filter(!is.na(Gender)) %>%
  group_by(target) %>%
  nest()

# run the anova on each data frame (the data in the 3rd column)
# map takes the data column, runs the analysis on the right, and saves results in the
# new column created by mutate
nested <- nested %>%
  mutate(model = map(data, ~aov(religion ~ Gender, data = .)))

# this creates a new column which is a dataframe of all the anova output
# nicely tidied up so you get the test statistics for each term
nested <- nested %>%
  mutate(tidy = map(model, broom::tidy))

#Here are the results
nested %>%
  unnest(tidy)

tab1 <- process_nested(nested,"nested1")

# Print the combined results table to view all ANOVA summaries 
print(tab1)

library(dplyr)
library(gt)

tab1_color<-tab1 %>%
  mutate(
    Gender.p.value = signif(Gender.p.value, 2)
  ) %>%
  gt() %>%
  fmt_number(
    columns = c("Gender.F", "Gender.p.value"),
    decimals = 2
  ) %>%
  data_color(
    columns = "Gender.p.value",
    colors = scales::col_bin(
      bins = c(-Inf, 0.05, Inf),
      palette = c("red", "black")
    )
  ) %>%
  cols_label(
    target = "Target",
    Gender.F = "F Statistic",
    Gender.p.value = "p-value"
  ) %>%
  tab_options(
    table.font.size=px(10)
  )

print(tab1_color)
```
#### Direction? {.tabset}

##### Celebrate {.tabset}

```{r, warning=FALSE}
t.test(subjects$ReligFreq_Celebrate~subjects$Gender) # F < M, p=0.03
effsize::cohen.d(subjects$ReligFreq_Celebrate~subjects$Gender) #d=0.12
#Girls celebrate less than boys (remember it's because its reversed)
```

##### ReligiousPlaces {.tabset}

```{r, warning=FALSE}
t.test(subjects$ReligFreq_ReligiousPlace~subjects$Gender) # F < M, p<0.001
effsize::cohen.d(subjects$ReligFreq_ReligiousPlace~subjects$Gender) #d=0.27
#Girls go to religious places less than boys (remember it's because its reversed)
```

### Religious differences {.tabset}

#### Do they Exist? {.tabset} 

```{r, warning=FALSE}
#ANOVAs to test: 

# nest by targets (which will be the outcomes of subsequent analyses)
nested <- religLong %>% 
  filter(relig %in% c('Hindu','Muslim')) %>%
  group_by(target) %>%
  nest()

# run the anova on each data frame (the data in the 3rd column)
# map takes the data column, runs the analysis on the right, and saves results in the
# new column created by mutate
nested <- nested %>%
  mutate(model = map(data, ~aov(religion ~ relig, data = .)))

# this creates a new column which is a dataframe of all the anova output
# nicely tidied up so you get the test statistics for each term
nested <- nested %>%
  mutate(tidy = map(model, broom::tidy))

#Here are the results
nested %>%
  unnest(tidy)

tab1 <- process_nested(nested,"nested1")

# Print the combined results table to view all ANOVA summaries 
print(tab1)

library(dplyr)
library(gt)

tab1_color<-tab1 %>%
  mutate(
    relig.p.value = signif(relig.p.value, 2)
  ) %>%
  gt() %>%
  fmt_number(
    columns = c("relig.F", "relig.p.value"),
    decimals = 2
  ) %>%
  data_color(
    columns = "relig.p.value",
    colors = scales::col_bin(
      bins = c(-Inf, 0.05, Inf),
      palette = c("red", "black")
    )
  ) %>%
  cols_label(
    target = "Target",
    relig.F = "F Statistic",
    relig.p.value = "p-value"
  ) %>%
  tab_options(
    table.font.size=px(10)
  )
print(tab1_color)
```
#### Direction? {.tabset}

##### Read {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$ReligFreq_Read~onlyMH$relig) # H < M, p<0.001
effsize::cohen.d(onlyMH$ReligFreq_Read~onlyMH$relig) #d=1.11
#Muslims read religious texts more than Hindus (remember it's because its reversed)
```
##### ReligiousPlace {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$ReligFreq_ReligiousPlace~onlyMH$relig) # H < M, p<0.001
effsize::cohen.d(onlyMH$ReligFreq_ReligiousPlace~onlyMH$relig) #d=0.235
#Muslims visit religious places more than Hindus (remember it's because its reversed)
```

##### Religiosity {.tabset}

```{r, warning=FALSE}
t.test(onlyMH$Religiosity_Religiosity~onlyMH$relig) # H < M, p<0.001
effsize::cohen.d(onlyMH$Religiosity_Religiosity~onlyMH$relig) #d=0.246
#Muslims report being more religious than Hindus (remember it's because its reversed)
```


## SOM8: Resouce Allocation

```{r, warning=FALSE}
# convert to long
dgLong <- subjects %>%
  dplyr::select(Subject.ID,grade,Gender,relig,ResourceAlloc_Friend:ResourceAlloc_Mohammed) %>%
  gather(target,rating,ResourceAlloc_Friend:ResourceAlloc_Mohammed) %>%
  mutate(target = substr(target,15,25),
         rating=rating-1)

table(dgLong$target) #sanity check
table(dgLong$rating)
```

```{r, warning=FALSE}
## Filters to keep only Hindus and Muslims, drops unused religions, and then splits by target (e.g., Krishna, Friend, etc.)
dgLongList <- dgLong %>%
  filter(relig %in% c('Hindu','Muslim'),!is.na(rating)) %>%
  mutate(relig = droplevels(relig)) %>%
  base::split(x= ., f=.$target, drop=TRUE)

library(ggplot2)
library(dplyr)
library(patchwork)  # for combining plots

# Make a custom plot function
make_plot <- function(df, title_text) {
  ggplot(df, aes(x = relig, y = rating, fill = relig)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.3, color = "black") +
    stat_summary(fun = mean, geom = "point", shape = 18, size = 3, color = "red") +
    labs(title = title_text, x = "Participant Religion", y = "Rating") +
    theme_minimal(base_size = 12) +
    scale_y_continuous(breaks = seq(0, 6, 1), limits = c(0, 6)) +
    theme(legend.position = "none",
          plot.title = element_text(hjust = 0.5))
}

# Filter the relevant data
dg_filtered <- dgLong %>%
  filter(relig %in% c("Hindu", "Muslim"), !is.na(rating)) %>%
  mutate(relig = droplevels(relig))

# Create one plot per target
plot_friend   <- make_plot(filter(dg_filtered, target == "Friend"), "Target: Friend")
plot_krishna  <- make_plot(filter(dg_filtered, target == "Krishna"), "Target: Krishna")
plot_mohammed <- make_plot(filter(dg_filtered, target == "Mohammed"), "Target: Mohammed")


combined_plot <- plot_friend + plot_krishna + plot_mohammed +
  plot_layout(nrow = 1, guides = "collect") +
  plot_annotation(title = "Hypothetical Resource Allocations by Target",
                  theme = theme(plot.title = element_text(color = "red", size = 14, hjust = 0.5)))

print(combined_plot)
```

### Age differences {.tabset}

```{r, warning=FALSE}
cor.test(subjects$ResourceAlloc_Friend,subjects$ageinyears) # p=0.05 
cor.test(subjects$ResourceAlloc_Krishna,subjects$ageinyears) # p=0.03 (more with age)
cor.test(subjects$ResourceAlloc_Mohammed,subjects$ageinyears) #p=0.10

```

### Gender differences {.tabset}

```{r, warning=FALSE}
t.test(ResourceAlloc_Friend ~ Gender, data=subjects) # p = 0.45
t.test(ResourceAlloc_Krishna ~ Gender, data=subjects) # p= 0.57
t.test(ResourceAlloc_Mohammed ~ Gender, data=subjects) # p=0.02 (boys more generous)
```

### Religious differences {.tabset}

```{r, warning=FALSE}
t.test(ResourceAlloc_Friend ~ relig, data=filter(subjects,relig %in% c("Hindu",'Muslim'))) # p =  0.91

t.test(ResourceAlloc_Krishna ~ relig, data=filter(subjects,relig %in% c("Hindu",'Muslim'))) # p<0.001 (Hindus more)
effsize::cohen.d(ResourceAlloc_Krishna ~ relig, data=filter(subjects,relig %in% c("Hindu",'Muslim')))

t.test(ResourceAlloc_Mohammed ~ relig, data=filter(subjects,relig %in% c("Hindu",'Muslim'))) # p<0.001 (Muslims more)
effsize::cohen.d(ResourceAlloc_Mohammed ~ relig, data=droplevels(filter(subjects,relig %in% c("Hindu",'Muslim')))) # d = -0.48

```

